### 2013-04-26 essay/main.tex
new python version

\documentclass[11pt, times]{article}
\usepackage{cite}
\usepackage[top=1in, bottom=0.75in, left=0.75in, right=0.75in]{geometry}
%\usepackage{pslatex}

\begin{document}

\title{The Impact of Cloud Computing in $10$ Years}
\author{Jilong Liao\\jliao2@utk.edu}
\date{\today}
\maketitle

\begin{abstract}
Cloud computing has been very active in both academia and industry field for several years. Major cloud computing vendors, like Amazon, Google and Dropbox, have provided users and businesses many advantages such as reliable and convenient storage, elastic computing power, and simple application deployment, lower IT infrastructure cost, etc. In $10$ years, I will expect cloud computing's influence far beyond the current achievements, but deeply inside mobile technology, scientific computing, massive online education and online-to-offline market. In this essay, I will discuss this point with my observations and understandings.
\end{abstract}

\input{tex/essay.tex}

\bibliographystyle{cls/model1-num-names}
\bibliography{reference}

\end{document}

### 2013-04-26 essay/tex/essay.tex
new python version

\section{Introduction}

\section{Mobile Computing and Cloud Computing}

\section{Massive Open Online Courses and Cloud Computing}

\section{Scientific Computing and Cloud Computing}

\section{Online-to-Offline Market and Cloud Computing}

\section{Conclusion}

### 2013-04-26 src/__init__.py

@@ -1,0 +1,12 @@
+'''
+	This package is related to CS594 Cloud Computing Course Project.
+	Author: Jilong Liao (jliao2@utk.edu)
+
+	The major work of this package is to design and implement a system
+	which could use the power of cloud computing to solve some very
+	hard problems quickly. For example, the 3-SAT, Traveling Salesman
+	Problem and Maximum Complete Subgraph.
+
+	For design details, please read the Cloud_Cache.pdf; for package
+	details, please read README.md
+'''

### 2013-04-26 src/configure.py

@@ -1,0 +1,16 @@
+'''
+	CS594 Cloud Computing Course Project.
+	Author: Jilong Liao (jliao2@utk.edu)
+
+	The global configuration file, both Master Node and Slave Nodes
+	rely on this file to configure the system.
+'''
+
+MASTER_NODE = ['localhost']
+SLAVE_NODE = ['localhost', 'localhost'
+			  'localhost', 'localhost']
+
+MASTER_PORT = 12530
+SLAVE_PORT = 12531
+
+

### 2013-04-26 src/jobs.py

@@ -1,0 +1,13 @@
+'''
+	CS594 Cloud Computing Course Project.
+	Author: Jilong Liao (jliao2@utk.edu)
+
+	This package defines the complete workflow of a Job. For example,
+	the 3-SAT problem, we may be asked to solve 1 million expressions,
+	then the complete job flow includes: load expression, solve single
+	expression with kernel-solver, and receive the results.
+'''
+
+
+class Base3SATJob(object):
+	pass

### 2013-04-26 src/kernel.py

@@ -1,0 +1,60 @@
+'''
+	CS594 Cloud Computing Course Project.
+	Author: Jilong Liao (jliao2@utk.edu)
+
+	The Kernel package is the place to define and implement any kind of
+	kernel-solver. Each task needs a kernel-solver to solve. The 
+	kernel-solver can use the cloud cache to speed up the process,
+	but it runs only on ONE machine. Cloud Cache provides the query APIs
+	to see if there is existing results in the cloud.
+'''
+
+
+class BaseKernel3SAT(object):
+	'''the brute-force approach to solve 3-SAT problem.'''
+	def __init__(self, task):
+		self._NumberOfVariable = eval(task.split(',')[0])
+		self._NumberOfExpression = eval(task.split('.')[1])
+		self._Expression = [eval(o) for o in task.split('.')[2:]]
+		self._Assignment = [False for o in range(self._NumberOfVariable)]
+		
+	def solve(self):
+		'''public interface for the base kernel-solver.'''
+		return self._RecurrsiveSolve(self._Expression, 0)
+
+	def _RecurrsiveSolve(self, assignment, index):
+		'''internal recurrsive solution.'''
+		if index == len(assignment):
+			result = self._AssignmentValidation(self._Expression, assignment)
+			if result:
+				return assignment
+			else:
+				return []
+		result = self._RecurrsiveSolve(assignment, index + 1)
+		if result != []:
+			return result
+		assignment[index] = (not assignment[index])
+		result = self._RecurrsiveSolve(assignment, index + 1)
+		if result != []:
+			return result
+		return []
+
+	def _AssignmentValidation(self, expression, assignment):
+		'''expression and assignment are lists.'''
+		result = True
+		for i in range(len(expression)/3):
+			a = expression[i*3]
+			b = expression[i*3 + 1]
+			c = expression[i*3 + 2]
+			va = assignment[abs(a)] if a > 0 else (not assignment[abs(a)])
+			vb = assignment[abs(b)] if b > 0 else (not assignment[abs(b)])
+			vc = assignment[abs(c)] if c > 0 else (not assignment[abs(c)])
+			result &= (va | vb | vc)
+			if not result:
+				return False
+		return True
+			
+
+
+class CloudCacheKernel3SAT(object):
+	pass

### 2013-04-26 src/master.py

@@ -1,0 +1,46 @@
+'''
+	CS594 Cloud Computing Course Project.
+	Author: Jilong Liao (jliao2@utk.edu)
+
+	This file is the Master Node design. The Master Node is used to
+	accept the job from the client, then distribute the jobs to many
+	different Slave Node. The Master Node needs to know the global
+	configuration of the system.
+
+	The Master Node has the two-way TCP communication between any
+	Slave Node. The communication port can be configured from the
+	configure.py.
+'''
+
+
+import socket
+import threading
+import SocketServer
+import tools
+import configure
+
+
+# Global variables.
+ExecutionBookKeeper = {}
+
+class MasterThreadedTcpHandler(SocketServer.BaseRequestHandler):
+	'''listen to the results from the Slave Node. '''
+	def handle(self):
+		pass
+
+
+class MasterThreadedTcpServer(SocketServer.ThreadingMixIn, SocketServer.TCPServer):
+	pass
+
+if __name__ == '__main__':
+	# start the Master Node as daemon.
+	MasterServer = MasterThreadedTcpServer((configure.MASTER_NODE[0], 
+		configure.MASTER_PORT), MasterThreadedTcpHandler)
+	MasterServerThread = threading.Thread(target=MasterServer.serve_forever)
+	MasterServerThread.daemon = True
+	MasterServerThread.start()
+
+	# start load job
+
+	# turn off Tcp server.
+	MasterServer.shutdown()

### 2013-04-26 src/slave.py

@@ -1,0 +1,44 @@
+'''
+	CS594 Cloud Computing Course Project.
+	Author: Jilong Liao (jliao2@utk.edu)
+
+	The Slave Node is the machine to run the job coming from the
+	Master Node. Besides, each Slave Node has a Redis server running
+	on localhost. The Redis Server is used to store the data which
+	has been previously calcuated, then the next time the Redis server
+	is able to provide the existing solutions for any <key, value> pair.
+
+	Slave Node is mutli-thread enabled in order to speed up the whole
+	batch process from the Master Node.
+
+	The Slave Node also has a two-way communication channel with the
+	Master Node. No automatical start process is provided at the current
+	stage, so the Slave Node needs to be turned on manually.
+'''
+
+
+import socket
+import threading
+import SocketServer
+import tools
+import configure
+
+
+class SlaveThreadedTcpRequestHandler(SocketServer.BaseRequestHandler):
+	'''The slave handler to run a single kernel-solver.'''
+	def handle(self):
+		pass
+
+
+class SlaveThreadedTcpServer(SocketServer.ThreadingMixIn, SocketServer.TCPServer):
+	pass
+
+
+if __name__ == '__main__':
+	# start the TCP server and always listen to the task from Master Node.
+	NetworkMgr = tools.LocalNetworkManager()
+	IpAddress = NetworkMgr.getLocalIpAddress()
+	SlaveServer = SlaveThreadedTcpServer((IpAddress, configure.SLAVE_PORT), 
+		SlaveThreadedTcpRequestHandler)
+	SlaveServerThread = threading.Thread(target=SlaveServer.serve_forever)
+	SlaveServerThread.start()

### 2013-04-26 src/tools.py

@@ -1,0 +1,61 @@
+'''
+	CS594 Cloud Computing Course Project.
+	Author: Jilong Liao (jliao2@utk.edu)
+
+	This package provides some tools such as load/store data, load balance,
+	hash functions, etc.
+'''
+
+
+import socket
+
+
+class JobDataHelper(object):
+	'''load/store job data'''
+	def loadFromDisk(self, uri):
+		'''the data will be string array, each string is a task.'''
+		data = []
+		with open(uri, 'r') as dataReader:
+			data = dataReader.readlines()
+		return data
+
+	def storeToDisk(self, data, uri):
+		'''write the string array data to the specific data URI.'''
+		dataWriter = open(uri, 'w')
+		for line in data:
+			dataWriter.write(line + '\n')
+
+
+class LoadBalanceHelper(object):
+	pass
+
+
+class HashFunctionProvider(object):
+	pass
+
+
+class MessageSender(object):
+	'''send a message to any destination through TCP connection.'''
+	def __init__(self, ip, port, message):
+		self._Ip = ip
+		self._Port = port
+		self._Message = message
+	
+	def send(self):
+		sendSocket = socket.socket(socket.AF_INET, socket.SOCK_STREAM)
+		sendSocket.connect((self._Ip, self._Port))
+		try:
+			sendSocket.sendall(message)
+		finally:
+			sendSocket.close()
+
+
+class LocalNetworkManager(object):
+	'''manage the local network environment, such as local IP address.'''
+	def getLocalIpAddress(self):
+		probeSocket = socket.socket(socket.AF_INET, socket.SOCK_DGRAM)
+		probeSocket.connect(("www.google.com",80))
+		IpAddress = probeSocket.getsockname()[0]
+		probeSocket.close()
+		return IpAddress
+

### 2013-04-26 src/external/3-sat-data.cc
fix bug for kernel-solver.

@@ -31,8 +31,8 @@ int main (int argc, char *argv[]) {
 		int NumberOfExpressions = 3 * (rand() % 30 + 1);
 		fprintf(fp, "%d,%d", NumberOfVariables, NumberOfExpressions);
 		for (int j = 0; j < NumberOfExpressions; ++j) {
-			int x = (rand() % 100000) % NumberOfVariables + 1;
-			if (rand() % 100 >= 50) x = -x;
+			int x = (rand() % 100000) % NumberOfVariables;
+			if (rand() % 100 >= 80) x = -x;
 			fprintf(fp, ",%d", x);
 		}
 		fprintf(fp, "\n");

### 2013-04-26 src/kernel.py

@@ -14,13 +14,17 @@ class BaseKernel3SAT(object):
 	'''the brute-force approach to solve 3-SAT problem.'''
 	def __init__(self, task):
 		self._NumberOfVariable = eval(task.split(',')[0])
-		self._NumberOfExpression = eval(task.split('.')[1])
-		self._Expression = [eval(o) for o in task.split('.')[2:]]
+		self._NumberOfExpression = eval(task.split(',')[1])
+		self._Expression = [eval(o) for o in task.split(',')[2:]]
 		self._Assignment = [False for o in range(self._NumberOfVariable)]
+		print 'n: ', self._NumberOfVariable
+		print 'm: ', self._NumberOfExpression
+		print self._Expression
+		print self._Assignment
 		
 	def solve(self):
 		'''public interface for the base kernel-solver.'''
-		return self._RecurrsiveSolve(self._Expression, 0)
+		return self._RecurrsiveSolve(self._Assignment, 0)
 
 	def _RecurrsiveSolve(self, assignment, index):
 		'''internal recurrsive solution.'''

### 2013-04-26 src/configure.py
finish the framework

@@ -6,11 +6,21 @@
 	rely on this file to configure the system.
 '''
 
-MASTER_NODE = ['localhost']
-SLAVE_NODE = ['localhost', 'localhost'
-			  'localhost', 'localhost']
+MASTER_NODE = ['10.208.175.127']
+SLAVE_NODE = ['10.198.129.131', '10.210.205.29', '10.96.37.25', '10.96.245.71']
 
 MASTER_PORT = 12530
 SLAVE_PORT = 12531
 
 
+SLAVE_STATUS_READY = '0'
+SLAVE_STATUS_BUSY = '1'
+SLAVE_STATUS_NOT_AVAILABLE = '2'
+
+
+TASK_STATUS_READY = '3'
+TASK_STATUS_WORKING = '4'
+TASK_STATUS_FINISHED = '5'
+
+JOB_DATA_INPUT_URI = 'external/3-sat.in'
+JOB_OUTPUT_URI = 'solution.txt'

### 2013-04-26 src/jobs.py

@@ -1,13 +1,0 @@
-'''
-	CS594 Cloud Computing Course Project.
-	Author: Jilong Liao (jliao2@utk.edu)
-
-	This package defines the complete workflow of a Job. For example,
-	the 3-SAT problem, we may be asked to solve 1 million expressions,
-	then the complete job flow includes: load expression, solve single
-	expression with kernel-solver, and receive the results.
-'''
-
-
-class Base3SATJob(object):
-	pass

### 2013-04-26 src/master.py

@@ -21,18 +21,74 @@ import configure
 
 
 # Global variables.
-ExecutionBookKeeper = {}
+TaskStatusTable = {}
+SlaveNodeStatusTable = {}
+TaskSolutionTable = {}
+JobProgress = 0
+
+def GlobalInitialization():
+	'''the global initialization function.'''
+	global TaskStatusTable = {}
+	global SlaveNodeStatusTable = {}
+	global TaskSolutionTable = {}
+	global JobProgress = 0
+
+class CloudCache3SATJob(object):
+	'''the brute-force 3-SAT batch job.'''
+	def __init__(self, inUri, outUri):
+		self._InputUri = inUri
+		self._OutputUri = outUri
+		self._Helper = tools.JobDataHelper()
+		self._Data = self._Helper.loadFromDisk(self._InputUri)
+	
+	def execute(self):
+		'''for each task, select proper Slave Node to execute.'''
+		while JobProgress < len(self._Data):
+			# select a task.
+			task = ''
+			for item in self._Data:
+				if item not in TaskStatusTable.keys():
+					task = item
+					break
+					
+			# select a Slave Node if possible.
+			selector = tools.SlaveNodeSelector(SlaveNodeStatusTable)
+			slave = selector.select()
+			if slave == configure.SLAVE_STATUS_NOT_AVAILABLE:
+				continue
+
+			# issue the task to slave, update the status information.
+			issuer = tools.TaskIssuer(slave, task)
+			issuer.issue()
+			TaskStatusTable[task] = configure.TASK_STATUS_WORKING
+			SlaveNodeStatusTable[slave] = configure.SLAVE_STATUS_BUSY
+			JobProgress += 1
+		# when finished, store the results to disk.
+		results = [TaskSolutionTable[task] for task in self._Data]
+		self._Helper.storeToDisk(results, self._OutputUri)
+
 
 class MasterThreadedTcpHandler(SocketServer.BaseRequestHandler):
-	'''listen to the results from the Slave Node. '''
+	'''listen to the results from the Slave Node and udpate the status.'''
 	def handle(self):
-		pass
+		# receive the <task, result> pair.
+		message = self.request.recv(4096).strip()
+		message = simplejson.load(message)
+		task = message['task']
+		result = message['result']
+		# update status.
+		TaskStatusTable[task] = configure.TASK_STATUS_FINISHED
[…]

### 2013-04-26 src/slave.py

@@ -22,12 +22,23 @@ import threading
 import SocketServer
 import tools
 import configure
+import simplejson
+import kernel
 
 
 class SlaveThreadedTcpRequestHandler(SocketServer.BaseRequestHandler):
 	'''The slave handler to run a single kernel-solver.'''
 	def handle(self):
-		pass
+		# receive and extract task.
+		message = self.request.recv(4096).strip()
+		task = simplejson.load(message)['task']
+		# run the kernel-solver for the task.
+		solver = kernel.BaseKernel3SAT(task)
+		result = solver.solve()
+		# report the results.
+		reporter = tools.TaskReporter(task, result)
+		reporter.report()
+
 
 
 class SlaveThreadedTcpServer(SocketServer.ThreadingMixIn, SocketServer.TCPServer):

### 2013-04-26 src/tools.py

@@ -8,6 +8,9 @@
 
 
 import socket
+import configure
+import simplejson
+import redis
 
 
 class JobDataHelper(object):
@@ -20,35 +23,67 @@ class JobDataHelper(object):
 		return data
 
 	def storeToDisk(self, data, uri):
-		'''write the string array data to the specific data URI.'''
+		'''write the result list to the specific data URI.'''
 		dataWriter = open(uri, 'w')
 		for line in data:
-			dataWriter.write(line + '\n')
+			dataWriter.write(self._serializeArray(line) + '\n')
+
+	def _serializeArray(self, array):
+		'''serialize the array to a string.'''
+		sequence = ''
+		for item in array:
+			sequence += str(array) + ','
+		return sequence[0:len(sequence)-1]
 
 
-class LoadBalanceHelper(object):
-	pass
-
-
-class HashFunctionProvider(object):
-	pass
-
-
-class MessageSender(object):
-	'''send a message to any destination through TCP connection.'''
-	def __init__(self, ip, port, message):
-		self._Ip = ip
-		self._Port = port
-		self._Message = message
+class SlaveNodeSelector(object):
+	'''the Slave Node selector for a task.'''
+	def __init__(self, status):
+		self._SlaveNodeStatusTable = status
 	
-	def send(self):
+	def select(self):
+		for slave in self._SlaveNodeStatusTable.keys():
+			if self._SlaveNodeStatusTable[slave] == configure.SLAVE_STATUS_READY:
+				return slave
+		return configure.SLAVE_STATUS_NOT_AVAILABLE
+
+
+class TaskIssuer(object):
+	'''issue the task to the Slave Node.'''
+	def __init__(self, slave, task):
+		self._Ip = slave
+		self._Port = configure.SLAVE_PORT
+		self._Task = self._serialzeTask(task)
+	
+	def _serializeTask(self, task):
+		return simplejson.dumps({'task':task})
+
+	def issue(self):
 		sendSocket = socket.socket(socket.AF_INET, socket.SOCK_STREAM)
 		sendSocket.connect((self._Ip, self._Port))
 		try:
-			sendSocket.sendall(message)
+			sendSocket.sendall(self._Task)
 		finally:
 			sendSocket.close()
 
+
+class TaskReporter(object):
+	'''report the task results to the Master Node'''
+	def __init__(self, task, result):
+		self._Ip = configure.MASTER_NODE[0]
+		self._Port = configure.MASTER_PORT
[…]

### 2013-04-27 src/master.py
resolve the python global variable issue.

@@ -28,10 +28,14 @@ JobProgress = 0
 
 def GlobalInitialization():
 	'''the global initialization function.'''
-	global TaskStatusTable = {}
-	global SlaveNodeStatusTable = {}
-	global TaskSolutionTable = {}
-	global JobProgress = 0
+	global TaskStatusTable
+	global SlaveNodeStatusTable
+	global TaskSolutionTable
+	global JobProgress
+	TaskStatusTable = {}
+	SlaveNodeStatusTable = {}
+	TaskSolutionTable = {}
+	JobProgress = 0
 
 class CloudCache3SATJob(object):
 	'''the brute-force 3-SAT batch job.'''

### 2013-04-27 src/configure.py
add logger and resolve the socket timeout issue.

@@ -6,7 +6,8 @@
 	rely on this file to configure the system.
 '''
 
-MASTER_NODE = ['10.208.175.127']
+#MASTER_NODE = ['10.208.175.127']
+MASTER_NODE = ['localhost']
 SLAVE_NODE = ['10.198.129.131', '10.210.205.29', '10.96.37.25', '10.96.245.71']
 
 MASTER_PORT = 12530
@@ -21,6 +22,9 @@ SLAVE_STATUS_NOT_AVAILABLE = '2'
 TASK_STATUS_READY = '3'
 TASK_STATUS_WORKING = '4'
 TASK_STATUS_FINISHED = '5'
+
+MASTER_PROBE_MESSAGE = '6'
+SLAVE_READY_MESSAGE = '7'
 
 JOB_DATA_INPUT_URI = 'external/3-sat.in'
 JOB_OUTPUT_URI = 'solution.txt'

### 2013-04-27 src/kernel.py

@@ -8,6 +8,11 @@
 	but it runs only on ONE machine. Cloud Cache provides the query APIs
 	to see if there is existing results in the cloud.
 '''
+import logging
+
+
+# setup logging.
+logging.basicConfig(level=logging.DEBUG)
 
 
 class BaseKernel3SAT(object):
@@ -17,11 +22,9 @@ class BaseKernel3SAT(object):
 		self._NumberOfExpression = eval(task.split(',')[1])
 		self._Expression = [eval(o) for o in task.split(',')[2:]]
 		self._Assignment = [False for o in range(self._NumberOfVariable)]
-		print 'n: ', self._NumberOfVariable
-		print 'm: ', self._NumberOfExpression
-		print self._Expression
-		print self._Assignment
-		
+		logging.info('BaseKernel 3-SAT initialized. n = %d, m = %d', 
+			self._NumberOfVariable, self._NumberOfExpression)
+			
 	def solve(self):
 		'''public interface for the base kernel-solver.'''
 		return self._RecurrsiveSolve(self._Assignment, 0)

### 2013-04-27 src/master.py

@@ -18,7 +18,11 @@ import threading
 import SocketServer
 import tools
 import configure
+import logging
 
+
+# setup logger.
+logging.basicConfig(level=logging.DEBUG)
 
 # Global variables.
 TaskStatusTable = {}
@@ -26,16 +30,26 @@ SlaveNodeStatusTable = {}
 TaskSolutionTable = {}
 JobProgress = 0
 
+# Global functions.
 def GlobalInitialization():
 	'''the global initialization function.'''
-	global TaskStatusTable
-	global SlaveNodeStatusTable
-	global TaskSolutionTable
-	global JobProgress
+	global TaskStatusTable, SlaveNodeStatusTable, TaskSolutionTable, JobProgress
 	TaskStatusTable = {}
 	SlaveNodeStatusTable = {}
 	TaskSolutionTable = {}
 	JobProgress = 0
+	logging.info('Global initialization finished ...')
+
+def SlaveNodeRegistration():
+	'''register the slave node initially.'''
+	global SlaveNodeStatusTable
+	NetworkMgr = tools.LocalNetworkManager()
+	for slave in configure.SLAVE_NODE:
+		if not NetworkMgr.probeHost(slave, configure.SLAVE_PORT):
+			continue
+		SlaveNodeStatTable[slave] = configure.SLAVE_STATUS_READY
+	logging.info('Slave Node Registration finished ...')
+
 
 class CloudCache3SATJob(object):
 	'''the brute-force 3-SAT batch job.'''
@@ -47,6 +61,7 @@ class CloudCache3SATJob(object):
 	
 	def execute(self):
 		'''for each task, select proper Slave Node to execute.'''
+		global TaskStatusTable, SlaveNodeStatusTable, TaskSolutionTable, JobProgress
 		while JobProgress < len(self._Data):
 			# select a task.
 			task = ''
@@ -60,13 +75,14 @@ class CloudCache3SATJob(object):
 			slave = selector.select()
 			if slave == configure.SLAVE_STATUS_NOT_AVAILABLE:
 				continue
-
+			
 			# issue the task to slave, update the status information.
 			issuer = tools.TaskIssuer(slave, task)
 			issuer.issue()
 			TaskStatusTable[task] = configure.TASK_STATUS_WORKING
 			SlaveNodeStatusTable[slave] = configure.SLAVE_STATUS_BUSY
 			JobProgress += 1
+			logging.info('Issue to Slave Node @ %s', slave)
[…]

### 2013-04-27 src/slave.py

@@ -24,6 +24,12 @@ import tools
 import configure
 import simplejson
 import kernel
+import logging
+import time
+
+
+# setup logging.
+logging.basicConfig(level=logging.DEBUG)
 
 
 class SlaveThreadedTcpRequestHandler(SocketServer.BaseRequestHandler):
@@ -31,10 +37,20 @@ class SlaveThreadedTcpRequestHandler(SocketServer.BaseRequestHandler):
 	def handle(self):
 		# receive and extract task.
 		message = self.request.recv(4096).strip()
+		
+		# special case for probe message.
+		if message == configure.MASTER_PROBE_MESSAGE:
+			self.request.sendall(configure.SLAVE_READY_MESSAGE)
+			return
+		
+		logging.info('Receive task from Master ...')
 		task = simplejson.load(message)['task']
 		# run the kernel-solver for the task.
 		solver = kernel.BaseKernel3SAT(task)
+		__start_timer__ = time.time() # statistics collection.
 		result = solver.solve()
+		__end_timer__ = time.time()
+		logging.info('Task finished, cost = %f ...', __end_timer__ - __start_timer__)
 		# report the results.
 		reporter = tools.TaskReporter(task, result)
 		reporter.report()

### 2013-04-27 src/tools.py

@@ -11,6 +11,11 @@ import socket
 import configure
 import simplejson
 import redis
+import logging
+
+
+# setup logger.
+logging.basicConfig(level=logging.DEBUG)
 
 
 class JobDataHelper(object):
@@ -20,6 +25,7 @@ class JobDataHelper(object):
 		data = []
 		with open(uri, 'r') as dataReader:
 			data = dataReader.readlines()
+		logging.info('Job data loaded, total tasks = %d', len(data))
 		return data
 
 	def storeToDisk(self, data, uri):
@@ -27,6 +33,7 @@ class JobDataHelper(object):
 		dataWriter = open(uri, 'w')
 		for line in data:
 			dataWriter.write(self._serializeArray(line) + '\n')
+		logging.info('Jon results stored, total results = %d', len(data))
 
 	def _serializeArray(self, array):
 		'''serialize the array to a string.'''
@@ -63,6 +70,8 @@ class TaskIssuer(object):
 		sendSocket.connect((self._Ip, self._Port))
 		try:
 			sendSocket.sendall(self._Task)
+		except socket.error:
+			logging.warn('Task issue failed because socket failure ...')
 		finally:
 			sendSocket.close()
 
@@ -82,6 +91,8 @@ class TaskReporter(object):
 		sendSocket.connect((self._Ip, self._Port))
 		try:
 			sendSocket.sendall(self._Report)
+		except socket.error:
+			logging.warn('Task report failed because socket failure ...')
 		finally:
 			sendSocket.close()
 
@@ -93,7 +104,19 @@ class LocalNetworkManager(object):
 		IpAddress = probeSocket.getsockname()[0]
 		probeSocket.close()
 		return IpAddress
-
+	
+	def probeHost(self, host, port):
+		probeSocket = socket.socket(socket.AF_INET, socket.SOCK_DGRAM)
+		probeSocket.settimeout(1.0) # timeout is set to be 1 second.
+		probeSocket.connect((host, port))
+		try:
+			probeSocket.sendall(configure.MASTER_PROBE_MESSAGE)
+			response = probeSocket.recv(1024).strip()
+			return True if response == configure.SLAVE_READY_MESSAGE else False
+		except socket.timeout:
+			logging.info('Slave Node probe failure: %s ', host)
+		finally:
+			probeSocket.close()
 
 class PersistentStorageManager(object):
 	'''manage the persistent key/value (both JSON strings) storage on Redis server.'''

### 2013-04-27 src/configure.py
configure ip for testing.

@@ -6,8 +6,8 @@
 	rely on this file to configure the system.
 '''
 
-#MASTER_NODE = ['10.208.175.127']
-MASTER_NODE = ['localhost']
+MASTER_NODE = ['10.208.175.127']
+#MASTER_NODE = ['localhost']
 SLAVE_NODE = ['10.198.129.131', '10.210.205.29', '10.96.37.25', '10.96.245.71']
 
 MASTER_PORT = 12530

### 2013-04-27 src/tools.py
log the slave local IP

@@ -102,6 +102,7 @@ class LocalNetworkManager(object):
 		probeSocket = socket.socket(socket.AF_INET, socket.SOCK_DGRAM)
 		probeSocket.connect(("www.google.com",80))
 		IpAddress = probeSocket.getsockname()[0]
+		logging.info('Slave Node service IP: %s', IpAddress)
 		probeSocket.close()
 		return IpAddress
 	

### 2013-04-27 src/configure.py
revise the EC2 domain name

@@ -6,9 +6,15 @@
 	rely on this file to configure the system.
 '''
 
-MASTER_NODE = ['10.208.175.127']
+#MASTER_NODE = ['10.208.175.127']
+#MASTER_NODE = ['domU-12-31-39-06-A8-71.compute-1.internal']
+MASTER_NODE = ['ec2-54-234-172-153.compute-1.amazonaws.com']
 #MASTER_NODE = ['localhost']
-SLAVE_NODE = ['10.198.129.131', '10.210.205.29', '10.96.37.25', '10.96.245.71']
+#SLAVE_NODE = ['10.198.129.131', '10.210.205.29', '10.96.37.25', '10.96.245.71']
+#SLAVE_NODE = ['domU-12-31-39-10-82-79.compute-1.internal', 'domU-12-31-39-09-CA-D3.compute-1.internal', 'domU-12-31-39-16-26-EF.compute-1.internal', 'domU-12-31-39-16-F6-BD.compute-1.internal']
+SLAVE_NODE = ['ec2-54-225-2-34.compute-1.amazonaws.com', 'ec2-54-242-129-207.compute-1.amazonaws.com', 'ec2-54-225-22-165.compute-1.amazonaws.com', 'ec2-50-16-144-197.compute-1.amazonaws.com']
+PRIVATE_TO_PUBLIC_TABLE = {'10.198.129.131':'ec2-54-225-2-34.compute-1.amazonaws.com', '10.210.205.29':'ec2-54-242-129-207.compute-1.amazonaws.com', '10.96.37.25':'ec2-54-225-22-165.compute-1.amazonaws.com', '10.96.245.71':'ec2-50-16-144-197.compute-1.amazonaws.com'}
+
 
 MASTER_PORT = 12530
 SLAVE_PORT = 12531

### 2013-04-27 src/tools.py
add private_to_public domain

@@ -104,7 +104,7 @@ class LocalNetworkManager(object):
 		IpAddress = probeSocket.getsockname()[0]
 		logging.info('Slave Node service IP: %s', IpAddress)
 		probeSocket.close()
-		return IpAddress
+		return configure.PRIVATE_TO_PUBLIC_TABLE[IpAddress]
 	
 	def probeHost(self, host, port):
 		probeSocket = socket.socket(socket.AF_INET, socket.SOCK_DGRAM)

### 2013-04-27 src/configure.py
local test pass, move to EC2 for testing

@@ -6,18 +6,19 @@
 	rely on this file to configure the system.
 '''
 
-#MASTER_NODE = ['10.208.175.127']
+MASTER_NODE = ['10.208.175.127']
 #MASTER_NODE = ['domU-12-31-39-06-A8-71.compute-1.internal']
-MASTER_NODE = ['ec2-54-234-172-153.compute-1.amazonaws.com']
+#MASTER_NODE = ['ec2-54-234-172-153.compute-1.amazonaws.com']
 #MASTER_NODE = ['localhost']
-#SLAVE_NODE = ['10.198.129.131', '10.210.205.29', '10.96.37.25', '10.96.245.71']
+SLAVE_NODE = ['10.198.129.131', '10.210.205.29', '10.96.37.25', '10.96.245.71']
 #SLAVE_NODE = ['domU-12-31-39-10-82-79.compute-1.internal', 'domU-12-31-39-09-CA-D3.compute-1.internal', 'domU-12-31-39-16-26-EF.compute-1.internal', 'domU-12-31-39-16-F6-BD.compute-1.internal']
-SLAVE_NODE = ['ec2-54-225-2-34.compute-1.amazonaws.com', 'ec2-54-242-129-207.compute-1.amazonaws.com', 'ec2-54-225-22-165.compute-1.amazonaws.com', 'ec2-50-16-144-197.compute-1.amazonaws.com']
-PRIVATE_TO_PUBLIC_TABLE = {'10.198.129.131':'ec2-54-225-2-34.compute-1.amazonaws.com', '10.210.205.29':'ec2-54-242-129-207.compute-1.amazonaws.com', '10.96.37.25':'ec2-54-225-22-165.compute-1.amazonaws.com', '10.96.245.71':'ec2-50-16-144-197.compute-1.amazonaws.com'}
+#SLAVE_NODE = ['ec2-54-225-2-34.compute-1.amazonaws.com', 'ec2-54-242-129-207.compute-1.amazonaws.com', 'ec2-54-225-22-165.compute-1.amazonaws.com', 'ec2-50-16-144-197.compute-1.amazonaws.com']
[…]

### 2013-04-27 src/kernel.py

@@ -9,10 +9,12 @@
 	to see if there is existing results in the cloud.
 '''
 import logging
+import tools
 
 
 # setup logging.
-logging.basicConfig(level=logging.DEBUG)
+FORMAT = '%(asctime)-15s %(message)s'
+logging.basicConfig(format=FORMAT, level=logging.DEBUG)
 
 
 class BaseKernel3SAT(object):
@@ -27,7 +29,11 @@ class BaseKernel3SAT(object):
 			
 	def solve(self):
 		'''public interface for the base kernel-solver.'''
-		return self._RecurrsiveSolve(self._Assignment, 0)
+		solution = self._RecurrsiveSolve(self._Assignment, 0)
+		storageMgr = tools.PersistentStorageManager()
+		storageMgr.push(self._Expression, solution)
+		logging.info('Solution cached in the Redis ...')
+		return solution
 
 	def _RecurrsiveSolve(self, assignment, index):
 		'''internal recurrsive solution.'''
@@ -60,8 +66,46 @@ class BaseKernel3SAT(object):
 			if not result:
 				return False
 		return True
-			
 
 
 class CloudCacheKernel3SAT(object):
-	pass
+	'''the cloud cache approach to solve the 3-SAT problem.'''
+	def __init__(self, task):
+		self._NumberOfVariable = eval(task.split(',')[0])
+		self._NumberOfExpression = eval(task.split(',')[1])
+		self._Expression = [eval(o) for o in task.split(',')[2:]]
+		self._Assignment = [False for o in range(self._NumberOfVariable)]
+		self._BaseKernel = BaseKernel3SAT(task)
+		logging.info('CloudCacheKernel 3-SAT initialized. n = %d, m = %d', 
+			self._NumberOfVariable, self._NumberOfExpression)
+
+	def solve(self):
+		# linear traverse the problem and query the Redis server.
+		storageMgr = tools.PersistentStorageManager()
+		for i in range(0, len(self._Expression), 3):
+			subtask = self._Expression[i:]
+			assignment = storageMgr.query(subtask)
+			if assignment == []:
+				return []
+			if assignment != None and self._AssignmentValidation(self._Expression, assignment):
+				storageMgr.push(self._Expression, assignment)
+				return assignment
+		# if query failed, then use base kernel to solve.
+		return self._BaseKernel.solve()
+
+	def _AssignmentValidation(self, expression, assignment):
[…]

### 2013-04-27 src/master.py

@@ -19,10 +19,12 @@ import SocketServer
 import tools
 import configure
 import logging
+import simplejson
 
 
 # setup logger.
-logging.basicConfig(level=logging.DEBUG)
+FORMAT = '%(asctime)-15s %(message)s'
+logging.basicConfig(format=FORMAT, level=logging.DEBUG)
 
 # Global variables.
 TaskStatusTable = {}
@@ -47,7 +49,7 @@ def SlaveNodeRegistration():
 	for slave in configure.SLAVE_NODE:
 		if not NetworkMgr.probeHost(slave, configure.SLAVE_PORT):
 			continue
-		SlaveNodeStatTable[slave] = configure.SLAVE_STATUS_READY
+		SlaveNodeStatusTable[slave] = configure.SLAVE_STATUS_READY
 	logging.info('Slave Node Registration finished ...')
 
 
@@ -94,14 +96,16 @@ class MasterThreadedTcpHandler(SocketServer.BaseRequestHandler):
 		global TaskStatusTable, SlaveNodeStatusTable, TaskSolutionTable, JobProgress
 		# receive the <task, result> pair.
 		message = self.request.recv(4096).strip()
-		message = simplejson.load(message)
+		message = simplejson.loads(message)
 		task = message['task']
 		result = message['result']
 		# update status.
 		TaskStatusTable[task] = configure.TASK_STATUS_FINISHED
-		SlaveNodeStatusTable[self.client_address[0]] = configure.SLAVE_NODE_READY
+		SlaveNodeStatusTable[self.client_address[0]] = configure.SLAVE_STATUS_READY
 		TaskSolutionTable[task] = result
-		logging.info('Receive solution updates from Slave Node %s', self.client_address[0])
+		JobProgress += 1
+		logging.info('Receive solution updates from Slave Node %s, total solved = %d', 
+			self.client_address[0], JobProgress)
 
 
 class MasterThreadedTcpServer(SocketServer.ThreadingMixIn, SocketServer.TCPServer):

### 2013-04-27 src/slave.py

@@ -29,7 +29,8 @@ import time
 
 
 # setup logging.
-logging.basicConfig(level=logging.DEBUG)
+FORMAT = '%(asctime)-15s %(message)s'
+logging.basicConfig(format=FORMAT, level=logging.DEBUG)
 
 
 class SlaveThreadedTcpRequestHandler(SocketServer.BaseRequestHandler):
@@ -37,23 +38,21 @@ class SlaveThreadedTcpRequestHandler(SocketServer.BaseRequestHandler):
 	def handle(self):
 		# receive and extract task.
 		message = self.request.recv(4096).strip()
-		
 		# special case for probe message.
 		if message == configure.MASTER_PROBE_MESSAGE:
 			self.request.sendall(configure.SLAVE_READY_MESSAGE)
-			return
-		
-		logging.info('Receive task from Master ...')
-		task = simplejson.load(message)['task']
-		# run the kernel-solver for the task.
-		solver = kernel.BaseKernel3SAT(task)
-		__start_timer__ = time.time() # statistics collection.
-		result = solver.solve()
-		__end_timer__ = time.time()
-		logging.info('Task finished, cost = %f ...', __end_timer__ - __start_timer__)
-		# report the results.
-		reporter = tools.TaskReporter(task, result)
-		reporter.report()
+		else:	
+			logging.info('Receive task from Master ...')
+			task = simplejson.loads(message)['task']
+			# run the kernel-solver for the task.
+			solver = kernel.CloudCacheKernel3SAT(task)
+			__start_timer__ = time.time() # statistics collection.
+			result = solver.solve()
+			__end_timer__ = time.time()
+			logging.info('Task finished, cost = %f ...', __end_timer__ - __start_timer__)
+			# report the results.
+			reporter = tools.TaskReporter(task, result)
+			reporter.report()
 
 
 
@@ -65,6 +64,7 @@ if __name__ == '__main__':
 	# start the TCP server and always listen to the task from Master Node.
 	NetworkMgr = tools.LocalNetworkManager()
 	IpAddress = NetworkMgr.getLocalIpAddress()
+	logging.info('** Slave Node service at %s:%d **', str(IpAddress), configure.SLAVE_PORT)
 	SlaveServer = SlaveThreadedTcpServer((IpAddress, configure.SLAVE_PORT), 
 		SlaveThreadedTcpRequestHandler)
 	SlaveServerThread = threading.Thread(target=SlaveServer.serve_forever)

### 2013-04-27 src/tools.py

@@ -15,7 +15,8 @@ import logging
 
 
 # setup logger.
-logging.basicConfig(level=logging.DEBUG)
+FORMAT = '%(asctime)-15s %(message)s'
+logging.basicConfig(format=FORMAT, level=logging.DEBUG)
 
 
 class JobDataHelper(object):
@@ -60,7 +61,7 @@ class TaskIssuer(object):
 	def __init__(self, slave, task):
 		self._Ip = slave
 		self._Port = configure.SLAVE_PORT
-		self._Task = self._serialzeTask(task)
+		self._Task = self._serializeTask(task)
 	
 	def _serializeTask(self, task):
 		return simplejson.dumps({'task':task})
@@ -82,9 +83,10 @@ class TaskReporter(object):
 		self._Ip = configure.MASTER_NODE[0]
 		self._Port = configure.MASTER_PORT
 		self._Report = self._serializeReport(task, result)
+		print self._Report
 	
 	def _serializeReport(self, task, result):
-		return simplejson.dumps({'task':self._Task, 'result':self._Result})
+		return simplejson.dumps({'task':task, 'result':result})
 
 	def report(self):
 		sendSocket = socket.socket(socket.AF_INET, socket.SOCK_STREAM)
@@ -104,30 +106,59 @@ class LocalNetworkManager(object):
 		IpAddress = probeSocket.getsockname()[0]
 		logging.info('Slave Node service IP: %s', IpAddress)
 		probeSocket.close()
-		return configure.PRIVATE_TO_PUBLIC_TABLE[IpAddress]
+		return IpAddress
 	
 	def probeHost(self, host, port):
+		print host, port
 		probeSocket = socket.socket(socket.AF_INET, socket.SOCK_DGRAM)
 		probeSocket.settimeout(1.0) # timeout is set to be 1 second.
 		probeSocket.connect((host, port))
 		try:
 			probeSocket.sendall(configure.MASTER_PROBE_MESSAGE)
-			response = probeSocket.recv(1024).strip()
-			return True if response == configure.SLAVE_READY_MESSAGE else False
+			return True
 		except socket.timeout:
 			logging.info('Slave Node probe failure: %s ', host)
+			return False
 		finally:
 			probeSocket.close()
 
 class PersistentStorageManager(object):
-	'''manage the persistent key/value (both JSON strings) storage on Redis server.'''
+	'''manage the persistent key/value storage on Redis server.'''
 	def __init__(self):
 		self._RedisConnector = redis.Redis()
 
 	def query(self, key):
[…]

### 2013-04-27 src/master.py
optimization for load balance

@@ -20,6 +20,7 @@ import tools
 import configure
 import logging
 import simplejson
+import time
 
 
 # setup logger.
@@ -30,26 +31,30 @@ logging.basicConfig(format=FORMAT, level=logging.DEBUG)
 TaskStatusTable = {}
 SlaveNodeStatusTable = {}
 TaskSolutionTable = {}
+SlaveNodeCheckinTable = {}
 JobProgress = 0
 
 # Global functions.
 def GlobalInitialization():
 	'''the global initialization function.'''
-	global TaskStatusTable, SlaveNodeStatusTable, TaskSolutionTable, JobProgress
+	global TaskStatusTable, SlaveNodeStatusTable, TaskSolutionTable, \
+		JobProgress, SlaveNodeCheckinTable
 	TaskStatusTable = {}
 	SlaveNodeStatusTable = {}
+	SlaveNodeCheckinTable = {}
 	TaskSolutionTable = {}
 	JobProgress = 0
 	logging.info('Global initialization finished ...')
 
 def SlaveNodeRegistration():
 	'''register the slave node initially.'''
-	global SlaveNodeStatusTable
+	global SlaveNodeStatusTable, SlaveNodeCheckinTable
 	NetworkMgr = tools.LocalNetworkManager()
 	for slave in configure.SLAVE_NODE:
 		if not NetworkMgr.probeHost(slave, configure.SLAVE_PORT):
 			continue
 		SlaveNodeStatusTable[slave] = configure.SLAVE_STATUS_READY
+		SlaveNodeCheckinTable[slave] = time.time()
 	logging.info('Slave Node Registration finished ...')
 
 
@@ -73,7 +78,7 @@ class CloudCache3SATJob(object):
 					break
 					
 			# select a Slave Node if possible.
-			selector = tools.SlaveNodeSelector(SlaveNodeStatusTable)
+			selector = tools.SlaveNodeSelector(SlaveNodeStatusTable, SlaveNodeCheckinTable)
 			slave = selector.select()
 			if slave == configure.SLAVE_STATUS_NOT_AVAILABLE:
 				continue
@@ -93,7 +98,8 @@ class CloudCache3SATJob(object):
 class MasterThreadedTcpHandler(SocketServer.BaseRequestHandler):
 	'''listen to the results from the Slave Node and udpate the status.'''
 	def handle(self):
-		global TaskStatusTable, SlaveNodeStatusTable, TaskSolutionTable, JobProgress
[…]

### 2013-04-27 src/slave.py

@@ -55,7 +55,6 @@ class SlaveThreadedTcpRequestHandler(SocketServer.BaseRequestHandler):
 			reporter.report()
 
 
-
 class SlaveThreadedTcpServer(SocketServer.ThreadingMixIn, SocketServer.TCPServer):
 	pass
 

### 2013-04-27 src/tools.py

@@ -46,14 +46,20 @@ class JobDataHelper(object):
 
 class SlaveNodeSelector(object):
 	'''the Slave Node selector for a task.'''
-	def __init__(self, status):
+	def __init__(self, status, checkin):
 		self._SlaveNodeStatusTable = status
+		self._SlaveNodeCheckinTable = checkin
 	
 	def select(self):
+		EarliestCheckin = None
+		SelectedSlave = configure.SLAVE_STATUS_NOT_AVAILABLE
+		print self._SlaveNodeStatusTable
+		print self._SlaveNodeCheckinTable
 		for slave in self._SlaveNodeStatusTable.keys():
-			if self._SlaveNodeStatusTable[slave] == configure.SLAVE_STATUS_READY:
-				return slave
-		return configure.SLAVE_STATUS_NOT_AVAILABLE
+			if self._SlaveNodeStatusTable[slave] == configure.SLAVE_STATUS_READY \
+				and (EarliestCheckin == None or self._SlaveNodeCheckinTable[slave] < EarliestCheckin):
+				SelectedSlave = slave
+		return SelectedSlave
 
 
 class TaskIssuer(object):
@@ -71,6 +77,7 @@ class TaskIssuer(object):
 		sendSocket.connect((self._Ip, self._Port))
 		try:
 			sendSocket.sendall(self._Task)
+			sendSocket.close()
 		except socket.error:
 			logging.warn('Task issue failed because socket failure ...')
 		finally:
@@ -93,6 +100,7 @@ class TaskReporter(object):
 		sendSocket.connect((self._Ip, self._Port))
 		try:
 			sendSocket.sendall(self._Report)
+			sendSocket.close()
 		except socket.error:
 			logging.warn('Task report failed because socket failure ...')
 		finally:
@@ -115,6 +123,7 @@ class LocalNetworkManager(object):
 		probeSocket.connect((host, port))
 		try:
 			probeSocket.sendall(configure.MASTER_PROBE_MESSAGE)
+			probeSocket.close()
 			return True
 		except socket.timeout:
 			logging.info('Slave Node probe failure: %s ', host)

### 2013-04-27 src/master.py
central control optimization and testing done.

@@ -79,7 +79,8 @@ class CloudCache3SATJob(object):
 					
 			# select a Slave Node if possible.
 			selector = tools.SlaveNodeSelector(SlaveNodeStatusTable, SlaveNodeCheckinTable)
-			slave = selector.select()
+			#slave = selector.select()
+			slave = selector.random()
 			if slave == configure.SLAVE_STATUS_NOT_AVAILABLE:
 				continue
 			
@@ -89,7 +90,8 @@ class CloudCache3SATJob(object):
 			TaskStatusTable[task] = configure.TASK_STATUS_WORKING
 			SlaveNodeStatusTable[slave] = configure.SLAVE_STATUS_BUSY
 			JobProgress += 1
-			logging.info('Issue to Slave Node @ %s', slave)
+			#logging.info('Issue to Slave Node @ %s', slave)
+			time.sleep(0.05)
 		# when finished, store the results to disk.
 		results = [TaskSolutionTable[task] for task in self._Data]
 		self._Helper.storeToDisk(results, self._OutputUri)
@@ -113,7 +115,6 @@ class MasterThreadedTcpHandler(SocketServer.BaseRequestHandler):
 		JobProgress += 1
 		logging.info('Receive solution updates from Slave Node %s, total solved = %d', 
 			self.client_address[0], JobProgress)
-		print SlaveNodeStatusTable
 
 
 class MasterThreadedTcpServer(SocketServer.ThreadingMixIn, SocketServer.TCPServer):
@@ -128,7 +129,7 @@ if __name__ == '__main__':
 	MasterServer = MasterThreadedTcpServer((configure.MASTER_NODE[0], 
 		configure.MASTER_PORT), MasterThreadedTcpHandler)
 	MasterServerThread = threading.Thread(target=MasterServer.serve_forever)
-	MasterServerThread.daemon = True
+	#MasterServerThread.daemon = True
 	MasterServerThread.start()
 
 	# start load job

### 2013-04-27 src/tools.py

@@ -12,6 +12,7 @@ import configure
 import simplejson
 import redis
 import logging
+import random
 
 
 # setup logger.
@@ -53,13 +54,14 @@ class SlaveNodeSelector(object):
 	def select(self):
 		EarliestCheckin = None
 		SelectedSlave = configure.SLAVE_STATUS_NOT_AVAILABLE
-		print self._SlaveNodeStatusTable
-		print self._SlaveNodeCheckinTable
 		for slave in self._SlaveNodeStatusTable.keys():
 			if self._SlaveNodeStatusTable[slave] == configure.SLAVE_STATUS_READY \
 				and (EarliestCheckin == None or self._SlaveNodeCheckinTable[slave] < EarliestCheckin):
 				SelectedSlave = slave
 		return SelectedSlave
+	
+	def random(self):
+		return random.choice(self._SlaveNodeStatusTable.keys())
 
 
 class TaskIssuer(object):

### 2013-04-28 src/configure.py
fully distributed version, ready for testing.

@@ -16,10 +16,15 @@ SLAVE_NODE = ['10.198.129.131', '10.210.205.29', '10.96.37.25', '10.96.245.71']
 #PRIVATE_TO_PUBLIC_TABLE = {'10.198.129.131':'ec2-54-225-2-34.compute-1.amazonaws.com', '10.210.205.29':'ec2-54-242-129-207.compute-1.amazonaws.com', '10.96.37.25':'ec2-54-225-22-165.compute-1.amazonaws.com', '10.96.245.71':'ec2-50-16-144-197.compute-1.amazonaws.com'}
 #MASTER_NODE = ['192.168.10.144']
 #SLAVE_NODE = ['192.168.10.144'] 
+#SINKER_NODE = ['192.168.10.144']
+#DATA_NODE = ['192.168.10.144']
+DATA_NODE = ['10.198.129.131', '10.210.205.29', '10.96.37.25', '10.96.245.71']
+SINKER_NODE = ['10.208.175.127']
+
 
 MASTER_PORT = 12535
 SLAVE_PORT = 12536
-
+SINKER_PORT = 12537
 
 SLAVE_STATUS_READY = '0'
 SLAVE_STATUS_BUSY = '1'
@@ -34,4 +39,7 @@ MASTER_PROBE_MESSAGE = '6'
 SLAVE_READY_MESSAGE = '7'
 
 JOB_DATA_INPUT_URI = 'external/3-sat.in'
-JOB_OUTPUT_URI = 'solution.txt'
+JOB_OUTPUT_URI = 'external/solution.out'
+
+COMMAND_3_SAT = '3-sat'
+REPORT_CHUNK_SIZE = 1000

### 2013-04-28 src/kernel.py

@@ -19,18 +19,20 @@ logging.basicConfig(format=FORMAT, level=logging.DEBUG)
 
 class BaseKernel3SAT(object):
 	'''the brute-force approach to solve 3-SAT problem.'''
-	def __init__(self, task):
+	def __init__(self, task, pool):
 		self._NumberOfVariable = eval(task.split(',')[0])
 		self._NumberOfExpression = eval(task.split(',')[1])
 		self._Expression = [eval(o) for o in task.split(',')[2:]]
 		self._Assignment = [False for o in range(self._NumberOfVariable)]
+		self._Pool = pool
 		logging.info('BaseKernel 3-SAT initialized. n = %d, m = %d', 
 			self._NumberOfVariable, self._NumberOfExpression)
 			
 	def solve(self):
 		'''public interface for the base kernel-solver.'''
 		solution = self._RecurrsiveSolve(self._Assignment, 0)
-		storageMgr = tools.PersistentStorageManager()
+		selector = tools.DataNodeSelector(self._Expression)
+		storageMgr = tools.PersistentStorageManager(self._Pool[selector.getDataNode()])
 		storageMgr.push(self._Expression, solution)
 		logging.info('Solution cached in the Redis ...')
 		return solution
@@ -70,25 +72,29 @@ class BaseKernel3SAT(object):
 
 class CloudCacheKernel3SAT(object):
 	'''the cloud cache approach to solve the 3-SAT problem.'''
-	def __init__(self, task):
+	def __init__(self, task, pool):
 		self._NumberOfVariable = eval(task.split(',')[0])
 		self._NumberOfExpression = eval(task.split(',')[1])
 		self._Expression = [eval(o) for o in task.split(',')[2:]]
 		self._Assignment = [False for o in range(self._NumberOfVariable)]
-		self._BaseKernel = BaseKernel3SAT(task)
+		self._BaseKernel = BaseKernel3SAT(task, pool)
+		self._Pool = pool
 		logging.info('CloudCacheKernel 3-SAT initialized. n = %d, m = %d', 
 			self._NumberOfVariable, self._NumberOfExpression)
 
 	def solve(self):
 		# linear traverse the problem and query the Redis server.
-		storageMgr = tools.PersistentStorageManager()
 		for i in range(0, len(self._Expression), 3):
 			subtask = self._Expression[i:]
+			selector = tools.DataNodeSelector(subtask)
+			storageMgr = tools.PersistentStorageManager(self._Pool[selector.getDataNode()])
[…]

### 2013-04-28 src/master.py

@@ -27,25 +27,12 @@ import time
 FORMAT = '%(asctime)-15s %(message)s'
 logging.basicConfig(format=FORMAT, level=logging.DEBUG)
 
-# Global variables.
-TaskStatusTable = {}
+
+# global varibles.
 SlaveNodeStatusTable = {}
-TaskSolutionTable = {}
 SlaveNodeCheckinTable = {}
-JobProgress = 0
 
-# Global functions.
-def GlobalInitialization():
-	'''the global initialization function.'''
-	global TaskStatusTable, SlaveNodeStatusTable, TaskSolutionTable, \
-		JobProgress, SlaveNodeCheckinTable
-	TaskStatusTable = {}
-	SlaveNodeStatusTable = {}
-	SlaveNodeCheckinTable = {}
-	TaskSolutionTable = {}
-	JobProgress = 0
-	logging.info('Global initialization finished ...')
-
+# global function.
 def SlaveNodeRegistration():
 	'''register the slave node initially.'''
 	global SlaveNodeStatusTable, SlaveNodeCheckinTable
@@ -66,75 +53,41 @@ class CloudCache3SATJob(object):
 		self._Helper = tools.JobDataHelper()
 		self._Data = self._Helper.loadFromDisk(self._InputUri)
 	
-	def execute(self):
-		'''for each task, select proper Slave Node to execute.'''
-		global TaskStatusTable, SlaveNodeStatusTable, TaskSolutionTable, JobProgress
-		while JobProgress < len(self._Data):
-			# select a task.
-			task = ''
-			for item in self._Data:
-				if item not in TaskStatusTable.keys():
-					task = item
-					break
-					
-			# select a Slave Node if possible.
-			selector = tools.SlaveNodeSelector(SlaveNodeStatusTable, SlaveNodeCheckinTable)
-			#slave = selector.select()
-			slave = selector.random()
-			if slave == configure.SLAVE_STATUS_NOT_AVAILABLE:
-				continue
-			
-			# issue the task to slave, update the status information.
-			issuer = tools.TaskIssuer(slave, task)
-			issuer.issue()
-			TaskStatusTable[task] = configure.TASK_STATUS_WORKING
-			SlaveNodeStatusTable[slave] = configure.SLAVE_STATUS_BUSY
-			JobProgress += 1
-			#logging.info('Issue to Slave Node @ %s', slave)
-			time.sleep(0.05)
-		# when finished, store the results to disk.
[…]

### 2013-04-28 src/sinker.py

@@ -1,0 +1,61 @@
+'''
+	CS594 Cloud Computing Course Project.
+	Author: Jilong Liao (jliao2@utk.edu)
+
+	The Sink Node is used to receive all the solutions comes out
+	of the Slave Node which is isolated from the Master Node.
+
+	The change of the design comes from a benchmark which indicates
+	the Master Node cannot bear the burden from many Slave Node. Then
+	the execution efficiency becomes slow.
+'''
+
+
+import socket
+import threading
+import SocketServer
+import tools
+import configure
+import logging
+import simplejson
+import time
+
+
+# setup logging.
+FORMAT = '%(asctime)-15s %(message)s'
+logging.basicConfig(format=FORMAT, level=logging.DEBUG)
+
+
+# global variable.
+DataSinkHandler = open(configure.JOB_OUTPUT_URI, 'a')
+
+
+class SinkerThreadedTcpHandler(SocketServer.BaseRequestHandler):
+	'''listen to the results from the Slave Node and udpate the status.'''
+	def handle(self):
+		# receive the <task, result> pair.
+		message = ''
+		while True:
+			chunk = self.request.recv(4096).strip()
+			if len(chunk) == 0:
+				break
+			message += chunk
+		# store.
+		helper = tools.JobDataHelper()
+		global DataSinkHandler
+		helper.sinkToDisk(message, DataSinkHandler)
+		logging.info('Receive solution updates from Slave Node %s', self.client_address[0])
+
+
+class SinkerThreadedTcpServer(SocketServer.ThreadingMixIn, SocketServer.TCPServer):
+	pass
+
+if __name__ == '__main__':
+	# start the Sinker Node as daemon.
+	NetworkMgr = tools.LocalNetworkManager()
+	IpAddress = NetworkMgr.getLocalIpAddress()
+	SinkerServer = SinkerThreadedTcpServer((IpAddress, configure.SINKER_PORT), 
+		SinkerThreadedTcpHandler)
+	logging.info('** Sinker Node running at %s:%d', str(IpAddress), configure.SINKER_PORT)
+	SinkerServerThread = threading.Thread(target=SinkerServer.serve_forever)
+	SinkerServerThread.start()

### 2013-04-28 src/slave.py

@@ -26,6 +26,7 @@ import simplejson
 import kernel
 import logging
 import time
+import redis
 
 
 # setup logging.
@@ -33,26 +34,50 @@ FORMAT = '%(asctime)-15s %(message)s'
 logging.basicConfig(format=FORMAT, level=logging.DEBUG)
 
 
+# global variable
+DataNodeConnectionPool = {}
+ReportChunk = ''
+ReportCounter = 0
+
+
+# global initialization
+def GlobalInitialization():
+	global DataNodeConnectionPool
+	for node in configure.DATA_NODE:
+		DataNodeConnectionPool[node] = redis.ConnectionPool(host=node)
+		logging.info('Estabilished Redis connection: %s', node)
+
+
 class SlaveThreadedTcpRequestHandler(SocketServer.BaseRequestHandler):
 	'''The slave handler to run a single kernel-solver.'''
 	def handle(self):
-		# receive and extract task.
-		message = self.request.recv(4096).strip()
-		# special case for probe message.
-		if message == configure.MASTER_PROBE_MESSAGE:
-			self.request.sendall(configure.SLAVE_READY_MESSAGE)
-		else:	
-			logging.info('Receive task from Master ...')
-			task = simplejson.loads(message)['task']
-			# run the kernel-solver for the task.
-			solver = kernel.CloudCacheKernel3SAT(task)
+		# receive and extrac the task chunk.
+		logging.info('Receive job from Master ...')
+		message = ''
+		while True:
+			chunk = self.request.recv(4096).strip()
+			message += chunk
+			if len(chunk) == 0:
+				break
+		
+		logging.info('Job has been received ...')
+		subjob = simplejson.loads(message)
+		# run the kernel-solver for each task.
+		global DataNodeConnectionPool, ReportCounter, ReportChunk
+		for task in subjob:
+			solver = kernel.CloudCacheKernel3SAT(task, DataNodeConnectionPool)
 			__start_timer__ = time.time() # statistics collection.
 			result = solver.solve()
 			__end_timer__ = time.time()
 			logging.info('Task finished, cost = %f ...', __end_timer__ - __start_timer__)
 			# report the results.
-			reporter = tools.TaskReporter(task, result)
-			reporter.report()
+			reporter = tools.TaskReporter()
+			if ReportCounter < configure.REPORT_CHUNK_SIZE:
[…]

### 2013-04-28 src/tools.py

@@ -30,12 +30,9 @@ class JobDataHelper(object):
 		logging.info('Job data loaded, total tasks = %d', len(data))
 		return data
 
-	def storeToDisk(self, data, uri):
-		'''write the result list to the specific data URI.'''
-		dataWriter = open(uri, 'w')
-		for line in data:
-			dataWriter.write(self._serializeArray(line) + '\n')
-		logging.info('Jon results stored, total results = %d', len(data))
+	def sinkToDisk(self, data, dataHandler):
+		'''write data (JSON string) to the specific data URI.'''
+		dataHandler.write(data + '\n')
 
 	def _serializeArray(self, array):
 		'''serialize the array to a string.'''
@@ -64,22 +61,21 @@ class SlaveNodeSelector(object):
 		return random.choice(self._SlaveNodeStatusTable.keys())
 
 
-class TaskIssuer(object):
+class JobDispatcher(object):
 	'''issue the task to the Slave Node.'''
-	def __init__(self, slave, task):
+	def __init__(self, slave, job):
 		self._Ip = slave
 		self._Port = configure.SLAVE_PORT
-		self._Task = self._serializeTask(task)
+		self._Job = self._serializeTask(job)
 	
-	def _serializeTask(self, task):
-		return simplejson.dumps({'task':task})
+	def _serializeTask(self, job):
+		return simplejson.dumps(job)
 
-	def issue(self):
+	def dispatch(self):
 		sendSocket = socket.socket(socket.AF_INET, socket.SOCK_STREAM)
 		sendSocket.connect((self._Ip, self._Port))
 		try:
-			sendSocket.sendall(self._Task)
-			sendSocket.close()
+			sendSocket.sendall(self._Job)
 		except socket.error:
 			logging.warn('Task issue failed because socket failure ...')
 		finally:
@@ -88,21 +84,22 @@ class TaskIssuer(object):
 
 class TaskReporter(object):
 	'''report the task results to the Master Node'''
-	def __init__(self, task, result):
-		self._Ip = configure.MASTER_NODE[0]
-		self._Port = configure.MASTER_PORT
-		self._Report = self._serializeReport(task, result)
-		print self._Report
+	def __init__(self):
+		self._Ip = configure.SINKER_NODE[0]
+		self._Port = configure.SINKER_PORT
 	
 	def _serializeReport(self, task, result):
 		return simplejson.dumps({'task':task, 'result':result})
 
-	def report(self):
+	def combine(self, chunk, task, result):
[…]

### 2013-04-28 src/sample-client.py
add sample-client for fully dist. version

@@ -1,0 +1,34 @@
+'''
+	CS594 Cloud Computing Course Project.
+	Author: Jilong Liao (jliao2@utk.edu)
+
+	The sample client script to run an 3-SAT solver. Before running the client,
+	one should load the data file to the Master Node, then once the Master Node
+	receive the client request, it will start the cloud-cache kernel solver.
+
+	If you are willing to solve other problem, write your kernel solver, then
+	give a command to your problem, run the client again. Your results are expected
+	to be in the Sinker Node.
+
+	Alternatively, if any NFS or HDFS environment is available, this framework
+	can benefit a lot and reduce a large amount of job distribution time. So the
+	throughput could be even higher.
+'''
+
+
+import socket
+import configure
+
+def command(ip, port, message):
+	sock = socket.socket(socket.AF_INET, socket.SOCK_STREAM)
+	sock.connect((ip, port))
+	try:
+		sock.sendall(message)
+	finally:
+		sock.close()
+
+
+if __name__ == '__main__':
+	command(configure.MASTER_NODE[0], 
+			configure.MASTER_PORT,
+			'3-sat')

### 2013-04-28 src/tools.py
EC2 testing and bug fix, add statistics feature.

@@ -116,7 +116,6 @@ class LocalNetworkManager(object):
 		return IpAddress
 	
 	def probeHost(self, host, port):
-		print host, port
 		probeSocket = socket.socket(socket.AF_INET, socket.SOCK_DGRAM)
 		probeSocket.settimeout(1.0) # timeout is set to be 1 second.
 		probeSocket.connect((host, port))

### 2013-04-28 src/configure.py
local test job distribution

@@ -6,20 +6,20 @@
 	rely on this file to configure the system.
 '''
 
-MASTER_NODE = ['10.208.175.127']
+#MASTER_NODE = ['10.208.175.127']
 #MASTER_NODE = ['domU-12-31-39-06-A8-71.compute-1.internal']
 #MASTER_NODE = ['ec2-54-234-172-153.compute-1.amazonaws.com']
 #MASTER_NODE = ['localhost']
-SLAVE_NODE = ['10.198.129.131', '10.210.205.29', '10.96.37.25', '10.96.245.71']
+#SLAVE_NODE = ['10.198.129.131', '10.210.205.29', '10.96.37.25', '10.96.245.71']
 #SLAVE_NODE = ['domU-12-31-39-10-82-79.compute-1.internal', 'domU-12-31-39-09-CA-D3.compute-1.internal', 'domU-12-31-39-16-26-EF.compute-1.internal', 'domU-12-31-39-16-F6-BD.compute-1.internal']
 #SLAVE_NODE = ['ec2-54-225-2-34.compute-1.amazonaws.com', 'ec2-54-242-129-207.compute-1.amazonaws.com', 'ec2-54-225-22-165.compute-1.amazonaws.com', 'ec2-50-16-144-197.compute-1.amazonaws.com']
 #PRIVATE_TO_PUBLIC_TABLE = {'10.198.129.131':'ec2-54-225-2-34.compute-1.amazonaws.com', '10.210.205.29':'ec2-54-242-129-207.compute-1.amazonaws.com', '10.96.37.25':'ec2-54-225-22-165.compute-1.amazonaws.com', '10.96.245.71':'ec2-50-16-144-197.compute-1.amazonaws.com'}
-#MASTER_NODE = ['192.168.10.144']
-#SLAVE_NODE = ['192.168.10.144'] 
-#SINKER_NODE = ['192.168.10.144']
-#DATA_NODE = ['192.168.10.144']
-DATA_NODE = ['10.198.129.131', '10.210.205.29', '10.96.37.25', '10.96.245.71']
-SINKER_NODE = ['10.208.175.127']
+MASTER_NODE = ['192.168.10.144']
+SLAVE_NODE = ['192.168.10.144'] 
+SINKER_NODE = ['192.168.10.144']
+DATA_NODE = ['192.168.10.144']
[…]

### 2013-04-28 src/external/3-sat-data.cc

@@ -21,7 +21,7 @@ using namespace std;
 
 
 int main (int argc, char *argv[]) {
-	int NumberOfCases = 1000000;
+	int NumberOfCases = 100;
 	if (argc == 3 && strcmp(argv[1], "-n") == 0)
 		NumberOfCases = atoi(argv[2]);
 	FILE *fp = fopen("3-sat.in", "w");

### 2013-04-29 src/configure.py
EC2 evaluation configure

@@ -6,20 +6,26 @@
 	rely on this file to configure the system.
 '''
 
-#MASTER_NODE = ['10.208.175.127']
+MASTER_NODE = ['10.215.114.14']
 #MASTER_NODE = ['domU-12-31-39-06-A8-71.compute-1.internal']
 #MASTER_NODE = ['ec2-54-234-172-153.compute-1.amazonaws.com']
 #MASTER_NODE = ['localhost']
-#SLAVE_NODE = ['10.198.129.131', '10.210.205.29', '10.96.37.25', '10.96.245.71']
+SLAVE_NODE = ['10.215.197.55', 
+			  '10.200.251.252', 
+			  '10.206.118.135', 
+			  '10.192.169.57']
 #SLAVE_NODE = ['domU-12-31-39-10-82-79.compute-1.internal', 'domU-12-31-39-09-CA-D3.compute-1.internal', 'domU-12-31-39-16-26-EF.compute-1.internal', 'domU-12-31-39-16-F6-BD.compute-1.internal']
 #SLAVE_NODE = ['ec2-54-225-2-34.compute-1.amazonaws.com', 'ec2-54-242-129-207.compute-1.amazonaws.com', 'ec2-54-225-22-165.compute-1.amazonaws.com', 'ec2-50-16-144-197.compute-1.amazonaws.com']
 #PRIVATE_TO_PUBLIC_TABLE = {'10.198.129.131':'ec2-54-225-2-34.compute-1.amazonaws.com', '10.210.205.29':'ec2-54-242-129-207.compute-1.amazonaws.com', '10.96.37.25':'ec2-54-225-22-165.compute-1.amazonaws.com', '10.96.245.71':'ec2-50-16-144-197.compute-1.amazonaws.com'}
-MASTER_NODE = ['192.168.10.144']
-SLAVE_NODE = ['192.168.10.144'] 
-SINKER_NODE = ['192.168.10.144']
-DATA_NODE = ['192.168.10.144']
-#DATA_NODE = ['10.198.129.131', '10.210.205.29', '10.96.37.25', '10.96.245.71']
-#SINKER_NODE = ['10.208.175.127']
+#MASTER_NODE = ['192.168.10.144']
+#SLAVE_NODE = ['192.168.10.144'] 
+#SINKER_NODE = ['192.168.10.144']
+#DATA_NODE = ['192.168.10.144']
+DATA_NODE = ['10.215.197.55', 
[…]

### 2013-04-29 src/configure.py
reconfigure sinker node

@@ -25,7 +25,7 @@ DATA_NODE = ['10.215.197.55',
 			  '10.200.251.252', 
 			  '10.206.118.135', 
 			  '10.192.169.57']
-SINKER_NODE = ['10.248.135.0']
+SINKER_NODE = ['10.248.127.58']
 
 
 MASTER_PORT = 12535

### 2013-04-29 src/configure.py
add collection uri

@@ -46,6 +46,7 @@ SLAVE_READY_MESSAGE = '7'
 
 JOB_DATA_INPUT_URI = 'external/3-sat.in'
 JOB_OUTPUT_URI = 'external/solution.out'
+RUNTIME_COLLECTION_URI = 'external/stat.out'
 
 COMMAND_3_SAT = '3-sat'
 REPORT_CHUNK_SIZE = 1000

### 2013-04-30 paper/tex/design.tex
design section done in paper.

\section{Framework Design}\label{sec:design}
\subsection{The Problem-Solution Abstraction}
Many different types of hard problem we encounter have various input structure. For instance, 3-SAT problem input a logic expression while Clique problem needs a graph structure. Those different types of inputs brings the challenges to the CloudCache framework, because it is possible the CloudCache framework host many different types of problems and solutions and the cache query operation need to find the exact solutions for a certain problem. If we do not have a uniform structure for the all problems, the complexity in localizing problems and its solutions will be very large.

In CloudCache framework, we propose the general \emph{key-value} objects as the abstractions of problem-solutions where problems are the \emph{key} objects and solutions are the \emph{value} objects. To store the key-value objects in the general storage system (e.g. MySQL, Redis and MongoDB), we serialize the keys and values to strings. In this way, the general storage system can easily index, search and maintain the problems and its solutions regardless what type of problem it is.

For a specific problem, like the 3-SAT problem, the developers can define their data structure at their own convenience. The CloudCache framework's cache \emph{query()} and \emph{push()} APIs will first serialize the developer defined data structure when calling both APIs.

\subsection{Core System Design}
\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{pics/workflow.pdf}
\caption{The Logic Diagram of CloudCache}
\label{fig:logic}
\end{figure}

The CloudCache framework (Fig.~\ref{fig:logic}) includes four types of nodes and three computation phases in the cloud infrastructure. The nodes are \emph{Master Node}, \emph{Slave Node}, \emph{Data Node} and \emph{Sink Node}; the three phases are \emph{Job Distribution Phase}, \emph{Task Solve Phase} and \emph{Solution Sink Phase}. In addition, the \emph{Client Problem} exists outside of the cloud infrastructure which needs to be submitted into the CloudCache framework.

The Master Node is the central control component of the whole framework. It accepts the job submission from the client problem and split the the job into several subjobs. Those subjobs will later be distributed to different Slave Nodes. For each of the task in the subjob which the Slave Node is received from the Master Node, the Slave Node will initiate a \emph{kernel-solver} for the task. The kernel-solver is the single execution box defined by the developers for a problem which performs the cache query and solve functions. When the kernel-solver starts execution, it uses the \emph{query()} API to check if the current problem already has a solution in the CloudCache. The query API uses a \emph{hash} function to select the dedicated Data Node where a part of existing solutions are stored. Once the Data Node has been identified, the Data Node will response with a solution if the problem has been solved or a NULL value.

Whether the kernel-solver find the existing solutions or solve it by itself, the solution for the assigned problem will be cached in the Data Node, selected by the same hash function. We use a hash function to shard the queries because we consider the load balance of the Data Node which is much busier than Slave Node or Master Node in the system. In addition to cache the problem's solution, the solution needs to report to the Sink Node where the client program will come and retrieve the final results for all tasks in the job after the system finish the job. Note that we only have single Sink Node while the each kernel-solver will report its results to the Sink Node, the pressure at the Sink Node is significant which defects the whole system's throughput. Therefore, we have a solution accumulator attached to each Slave Node. The solution will be accumulated into a certain amount, then the Slave Node will report the results once.

\subsection{Framework Generalness}
An expected design goal of CloudCache is the generalness, we want to make this framework to be an proper and simply approach to solve many different types of hard problems in the cloud. According to the design, only two things need to be defined by the developer before using the framework. First, the problem and solution's data structure; second, the kernel-solver of the problem, namely when to query the cache and when to solve the problem by itself. After finishing the two parts, the developer can submit a batch of problem as a job to the Master Node, where each problem is regarded as a task. Then the framework will start executing the batch job. In this section, we will show three hard problems' solution using CloudCache's framework.

\subsubsection{3-SAT Problem}
The 3-SAT problem has an input of an boolean expression which contains many boolean variables' combinations in 3-conjunctive-normal-form clauses. For example, Eq.~\ref{eq:3-sat} shows an example 3-SAT problem which has $5$ boolean variables and has three clauses. For this problem, we use the expression vector as the key, but the vector is in a specific format. The boolean variable's index represents the variable itself in the vector, and the the index is set to be negative is the boolean variable has a ``not'' operator. The elements in expression are separated by a comma. Therefore, the \emph{key} for Eq.~\ref{eq:3-sat} is $[1,2,-3,2,3,4,3,-4,5]$.

\begin{equation}
Y = (x_1 \vee x_2 \vee \overline{x_3}) \wedge (x_2 \vee x_3 \vee x_4) \wedge (x_3 \vee \overline{x_4} \vee x_5)
\label{eq:3-sat}
\end{equation}

On the other hand, the solution of the problem is a vector of assignment, indicating each boolean variable's value as true or false. So for the 3-SAT problem instance in Eq.~\ref{eq:3-sat}, the \emph{value} is $[true, true, false, true, false]$. Once the key-value pair has been designed, we can move on to the \emph{kernel-solver} part.

The kernel-solver has two stages, the first stage is to check if the expression or any subexpression has been solved. We use a linear scan to do it by moving the head clause and check the subexpression between the head clause and the end one. For the example in Eq.~\ref{eq:3-sat}, we will check Eq.~\ref{eq:3-sat1},~\ref{eq:3-sat2},~\ref{eq:3-sat3}. If any of the subexpression has been solved, we will retrieve its solution then validate if the assignment can satisfy the whole expression. If so, we do not need a brute-force method to solve it again but just return the assignment in the cache. Otherwise, the brute-force method has to be run and we need to store the solved assignment in the cache. The two simple APIs to query and store key/value in the CloudCache make the operations very easy to do.

Note that we do not enumerate the possible combination of clauses in the expression to query the cache. The major reason is that most of the 3-SAT is not as hard as we may expect, thus the enumeration process may cost more time than a simple brute-force try. Besides, we cannot estimate the cache hit ratio for a clause combination ahead which may make the solution even slower as well.

\begin{equation}
Y = (x_1 \vee x_2 \vee \overline{x_3}) \wedge (x_2 \vee x_3 \vee x_4) \wedge (x_3 \vee \overline{x_4} \vee x_5)
\label{eq:3-sat1}
\end{equation}
\begin{equation}
Y = (x_2 \vee x_3 \vee x_4) \wedge (x_3 \vee \overline{x_4} \vee x_5)
\label{eq:3-sat2}
\end{equation}
\begin{equation}
Y = (x_3 \vee \overline{x_4} \vee x_5)
\label{eq:3-sat3}
\end{equation}

\subsubsection{k-coloring Problem}
The graph's k-coloring problem is to find a color assignment strategy that mark the vertex of the graph so that no adjacent vertex share the same color by using no more than k different colors. The problem is also a classic NP-Complete problem, the exact solution is a brute-force one by enumerating the $k^n$ assignments and validate them.

Similarly, we first need to abstract the problem-solution pairs. For the problem, we use a matrix $\mathbf{R}_{n\times n}$ to represent the graph which is the \emph{key}, and the \emph{value} is the color assignment vector $\mathbf{a} = [a_1, a_2, ..., a_n]$ where $n$ is the number of vertex in the graph.

The kernel-solver is also using a linear scan to all the vertices. For each vertex, we remove the edges connected to the vertex, then we have a new adjacent matrix $\hat{\mathbf{R}}_{(n-1)\times (n-1)}$ which is actually a subgraph of the original one. For this subgraph, we query the CloudCache to retrieve the existing color assignment. If success, we need to validate the assignment by enumerating the color of the removed vertex combining with the existing solution to see if the complete assignment can fit into the original graph. If so, we can cache the solution; if not, we continue removing another vertex in $\mathbf{R}_{n\times n}$ until we scan all the vertices one time. If cache is not working at all, the brute-force solver is triggered.

### 2013-04-30 paper/tex/implementation.tex
design section done in paper.

\section{Implementations}\label{sec:implementation}

### 2013-04-30 paper/tex/introduction.tex
design section done in paper.

\section{Introduction}\label{sec:introduction}
Cloud computing has become one of the most powerful tools which could potentially help people solve some extremely hard problems. The computation and storage resource in the cloud are relatively cheap and convenient comparing to build something from the scratch. Besides, the public cloud vendors, like Amazon and Google, have made its own powerful computation and storage infrastructure available to the public via cloud computing service. Those cloud vendors provide either virtual machines or pre-defined cloud APIs to help people build application on top of their cloud very easy and fast.

By the booming time of cloud computing, people may have the chance to rethink of the way to solve some existing hard problems in computer science. The hard problems (usually belongs to the NP-Complete category like 3-SAT) often require exponential computation time to traverse the solution space in a brute-force manner. In addition, people may need to solve the same types of problems again and again in different instance. Some instances or subproblems possibly have been solved by others. Therefore, we come to the idea that \emph{cache the existing solutions to those problems and query the solutions before we solve any other problems}.

One immediate challenge of this idea is the storage requirement. Even the same type of problem, e.g. 3-SAT, could have numerous problem instance, which may require several disks to store them, let alone we have many different types of hard problems. Cloud computing, at this point, could be a proper plagiarism because it is much less expensive to build a large scale storage and its management system. The other challenge is how we abstract the hard problems in a way that the platform we build could be more general to many different type of hard problems.

In this document, we propose \emph{CloudCache} framework which is built on top of general cloud computing platform and provides the interface to query, cache and solve hard problems in an easier way. The CloudCache framework abstracts the \emph{problem-solution} pair into \emph{key-value} objects, and uses some object storage system to cache existing problems and solutions. Further, the CloudCache framework provides a general problem solving interface \emph{kernel-solver}, so that the developer can easily write a problem's solution and solve it within the CloudCache's framework. CloudCache executes kernel-solver in a distributed way which tries to maximize the framework's problem solving throughput.

The rest of the document is arranged in the following way: Section~\ref{sec:design} describes the design and reasoning of the CloudCache framework; Section~\ref{sec:implementation} shows the implementations of the framework; Section~\ref{sec:evaluation} deploys the framework in Amazon EC2 and solves $1,000,000$ 3-SAT problem instances; Finally, we discuss some potential improvements and conclusion in Section~\ref{sec:conclusion}.

### 2013-04-30 paper/tex/implementation.tex
implementation is done.

@@
 \section{Implementations}\label{sec:implementation}
+In this section, we describe the implementation details of the CloudCache framework.
+Specifically, we will use the 3-SAT problem as the sample to illustrate the infrastructure, software architecture, and programming interface.
+
+\subsection{The CloudCache Infrastructure}
+As is shown in Fig.~\ref{fig:system}, the infrastructure in the cloud consists of four different types of nodes: Master Node, Slave Node, Data Node and Sink Node.
+Outside of the cloud infrastructure, we have a Client which will submit the job to the Master Node.
+After the job is done, the Sink Node will push the job results to the Client.
+
+The Master Node runs a multi-threaded TCP server, waiting for the job submitted from the Client.
+We consider the possibility of concurrent job submission from the clients, then the multi-threaded server is required.
+However, we do not optimize the server's performance under some pressure test.
+The Slave Node is also a multi-threaded TCP server, but once the Slave Node receives the job distributed from the Master Node, it will fork a worker thread to execute every task in the job.
+We do not fork multiple threads for each task because we do not want the first arrive job's tasks overwhelm the Slave Node (it is possible for Slave Node to run different jobs concurrently).
+
+The Data Node is a tricky part in the system, because we combine the Slave Node and Data Node together in single physical machine.
+So a machine in the cloud will both solve the problem and host the data.
+We use hash function to shard the solution's cache choice.
+The reason for this implementation is that we want to maximize the possibility of local cache query and avoid unnecessary and frequent remote cache check which is very time consuming.
+In addition, we do not choose SQL database such as MySQL as the local storage system, but use some NoSQL techniques such as Redis~\cite{macedo2011redis} to be the persistent data storage.
+We believe the NoSQL techniques have much better performance to manage the key/value objects.
+
+Finally, the Sink Node is the one to collect all the results and provide the final job result to the Client.
+To avoid the Slave Node's highly frequent task report, we buffer the report at the Slave Node until the buffer is full.
+This small optimization reduce the load of Sink Node, and increase the Slave Node's efficiency as well (task reporting blocks the Slave Node moving forward).
+
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{pics/cloud-cache-arch.pdf}
+\caption{The CloudCache System Diagram}
+\label{fig:system}
+\end{figure}
+
+\subsection{Software Architecture}
+We use Python as the language to implement the system. It consists of seven major modules in the source code.
+
+\begin{itemize}
+\item master.py. This module is the component to start a Master Node, which contains a multi-threaded TCP server, job class and some global variables for bookkeeping and statistics.
+
+\item slave.py. This module is the component to start a Slave Node. It includes a multi-threaded TCP server as well, and a job execution handler and some statistic variables.
+\item sink.py. The Sink Node module which receives the accumulated task report and dump the solutions to disk. After the job finished, the Client can come to retrieve the results.
+\item kernel.py. The core module to kernel-solver. A developer should define a class to solve the problem, then the Slave Node will call the kernel-solver based on the configuration.
+\item tools.py. It defines many helper class to help simplify the architecture like JobDispatcher, etc.
+\item configure.py. The place is used to define any global configuration details, for instance, the Master Node, Slave Node, Data Node and Sink Node.
+\end{itemize}
+
+For the Redis server, it has to be deployed before running any module in the Data Node.
+Since we combine the Data Node and Slave Node into one physical machine, the Redis server is running as a service in the operating system.
+
+\subsection{Programming Interface}
+Two important programming interface in the CloudCache is in the tools.py module.
+The two APIs are \emph{tools.PersistentStorageManager.query(key)} and \emph{tools.PersistentStorageManager.push(key, value)}.
+
+A developer can call these two APIs to simply the cache operations in the implementation of kernel-solver.
+The kernel-solver is an abstract name, however, in practice, a developer needs to implement the solver class.
+For example, the 3-SAT problem, we implement \emph{BaseKernel3SAT} and \emph{CloudCacheKernel3SAT} classes which will be instantiated in job execution handler.
+Again, the developer does not need to pay additional attention to the data structure of key and value, because the two APIs above will serialize the key and value first before conducting cache operations.

### 2013-04-30 src/configure.py
base-kernel experiment setup.

@@ -47,6 +47,7 @@ SLAVE_READY_MESSAGE = '7'
 JOB_DATA_INPUT_URI = 'external/3-sat.in'
 JOB_OUTPUT_URI = 'external/solution.out'
 RUNTIME_COLLECTION_URI = 'external/stat.out'
+CACHE_STATISTICS_URI = 'external/cache.out'
 
 COMMAND_3_SAT = '3-sat'
 REPORT_CHUNK_SIZE = 1000

### 2013-04-30 src/kernel.py

@@ -10,6 +10,7 @@
 '''
 import logging
 import tools
+import csv
 
 
 # setup logging.
@@ -83,6 +84,8 @@ class CloudCacheKernel3SAT(object):
 			self._NumberOfVariable, self._NumberOfExpression)
 
 	def solve(self):
+		# setup a statistics for cache hit rate.
+		stat = csv.writer(open(configure.CACHE_STATISTICS_URI, 'a'), delimiter=',')
 		# linear traverse the problem and query the Redis server.
 		for i in range(0, len(self._Expression), 3):
 			subtask = self._Expression[i:]
@@ -91,12 +94,15 @@ class CloudCacheKernel3SAT(object):
 			assignment = storageMgr.query(subtask)
 			if assignment == []:
 				logging.info('*** Cache Hit! ***')
+				stat.writerow([time.time(), 1])
 				return []
 			if assignment != None and self._AssignmentValidation(self._Expression, assignment):
 				storageMgr.push(self._Expression, assignment)
 				logging.info('*** Cache Hit! ***')
+				stat.writerow([time.time(), 1])
 				return assignment
 		# if query failed, then use base kernel to solve.
+		stat.writerow([time.time(), 0])
 		return self._BaseKernel.solve()
 
 	def _AssignmentValidation(self, expression, assignment):

### 2013-04-30 src/slave.py

@@ -70,7 +70,8 @@ class SlaveThreadedTcpRequestHandler(SocketServer.BaseRequestHandler):
 		# run the kernel-solver for each task.
 		global DataNodeConnectionPool, ReportCounter, ReportChunk
 		for task in subjob:
-			solver = kernel.CloudCacheKernel3SAT(task, DataNodeConnectionPool)
+			#solver = kernel.CloudCacheKernel3SAT(task, DataNodeConnectionPool)
+			solver = kernel.BaseKernel3SAT(task, DataNodeConnectionPool)
 			__start_timer__ = time.time() # statistics collection.
 			result = solver.solve()
 			__end_timer__ = time.time()

### 2013-04-30 paper/tex/performance.tex
framework performance

\section{Evaluations} \label{sec:evaluation}
To evaluate the performance of the CloudCache and validate whether the cache idea is feasible in reality, we deploy the CloudCache framework to Amazon EC2 platform in a small scale (Fig.~\ref{fig:ec2}). In the deployment, there are $1$ Master Node, $4$ Slave Node/Data Node, and $1$ Sink Node. All EC2 instance are micro which have the specifications in Table~\ref{tab:ec2}.

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{pics/deployment.png}
\caption{The EC2 instances in deployment}
\label{fig:ec2}
\end{figure*}

\begin{table}
\centering
\caption{EC2 Instance Specifications}
\begin{tabular}{ll}\toprule
Memory & $613$MB \\
Compute Units & up to $2$ \\
Operating System & Ubuntu 12.04 LTS 64-bit \\
I/O Performance & Low \\\bottomrule
\end{tabular}
\label{tab:ec2}
\end{table}

Additionally, we run a standard benchmark for Redis server on the Data Node. The results are shown in Table~\ref{}.

Then we randomly generate $1,000,000$ 3-SAT problem instances, then the Client node submit those problem instances as a job to the Master Node. The Slave Node start solving the problem using kernel-solver and we collect the runtime statistics for the problem solving time and cache hit rate. Further, we use the Amazon CloudWatch as the system performance monitor tool to track the CPU usage and network consumption inside the framework.

\subsection{Problem Solving Performance}

\subsection{Framework Performance}
First, we look at the Master Node. Fig.~\ref{fig:master_cpu} gives the CPU performance dynamics along with the whole process. As we can see, there are only several time points that the CPU cost of the Master Node is significant which include job distribution and its TCP server. Most of the time, the CPU cost in Master Node can be ignored which gives the opportunity that the Master Node can continue accepting other job submisions. The In-network (Fig.~\ref{fig:master_in}) and out-network (Fig.~\ref{fig:master_out}) performance shows there is no long-term major network activities in the Master Node, except for the job distribution phase.

Second, we take a Slave Node's tracking results. As is shown in Fig.~\ref{fig:slave_cpu}, the Slave Node's CPU reaches to full load right after the job distribution phase of Master Node. During the next several hours, the Slave Node is busy solving problem assigned to itself. From Fig.~\ref{fig:slave_in} we can see the job receiving's in-network fringerprints. Once the Slave Node starts working, the out-network starts increase because the generated solutions will be sinked to the Sink Node. Thus, as is illustrated in Fig.~\ref{fig:slave_out}, the out-network starts busy right after the Slave Node starts working. Besides, the trends to grow in out-network indicates the problem solving throughput increases and it takes less and less time to solve a problem when we cache more and more solutions. However, the grows are sub-linear as $O(log^n)$ where $n$ is the number solutions cached. A possible reason is the EC2 instance type become a bottleneck for this framework.

Finally, the Sinker Node's CPU (Fig.~\ref{fig:sinker_cpu}) is in mild load because we adopt the solution report buffer in the Slave Node. The in-network (Fig.~\ref{fig:sinker_in}) confirms the conclusions that the framework is speeding up the problem solution as a whole, because the increase in the in-network has the same grow style with Slave Node's out-network. The Sinker Node's out-network (Fig.~\ref{fig:sinker_out}) also shows the ACKs for receiving data from TCP which has the similar shape with the in-network.

\begin{figure*}[!htb]
\minipage{0.33\textwidth}
  \includegraphics[width=\linewidth]{pics/master_cpu.png}
  \caption{Master Node CPU}\label{fig:master_cpu}
\endminipage\hfill
\minipage{0.33\textwidth}
  \includegraphics[width=\linewidth]{pics/master_network_in.png}
  \caption{Master Node Network In}\label{fig:master_in}
\endminipage\hfill
\minipage{0.33\textwidth}
  \includegraphics[width=\linewidth]{pics/master_network_out.png}
  \caption{Master Node Network Out}\label{fig:master_out}
\endminipage\hfill
\end{figure*}

\begin{figure*}[!htb]
\minipage{0.33\textwidth}
  \includegraphics[width=\linewidth]{pics/slave_cpu.png}
  \caption{Slave Node CPU}\label{fig:slave_cpu}
\endminipage\hfill
\minipage{0.33\textwidth}
  \includegraphics[width=\linewidth]{pics/slave_network_in.png}
  \caption{Slave Node Network In}\label{fig:slave_in}
\endminipage\hfill
\minipage{0.33\textwidth}
  \includegraphics[width=\linewidth]{pics/slave_network_out.png}
  \caption{Slave Node Network Out}\label{fig:slave_out}
\endminipage\hfill
\end{figure*}

\begin{figure*}[!htb]
\minipage{0.33\textwidth}
  \includegraphics[width=\linewidth]{pics/sinker_cpu.png}
  \caption{Sinker Node CPU}\label{fig:sinker_cpu}
\endminipage\hfill
\minipage{0.33\textwidth}
  \includegraphics[width=\linewidth]{pics/sinker_network_in.png}
  \caption{Sinker Node Network In}\label{fig:sinker_in}
\endminipage\hfill
\minipage{0.33\textwidth}
  \includegraphics[width=\linewidth]{pics/sinker_network_out.png}
  \caption{Sinker Node Network Out}\label{fig:sinker_out}
\endminipage\hfill
\end{figure*}

### 2013-04-30 paper/data/runtime_analysis.m

@@ -1,0 +1,23 @@
+clear all;
+slave1 = load('stat_slave_1.out');
+slave2 = load('stat_slave_2.out');
+slave3 = load('stat_slave_3.out');
+slave4 = load('stat_slave_4.out');
+
+runtime1 = slave1(:,1) - slave1(:,2);
+runtime2 = slave2(:,1) - slave2(:,2);
+runtime3 = slave3(:,1) - slave3(:,2);
+runtime4 = slave4(:,1) - slave4(:,2);
+
+
+[r1, x1] = ecdf(runtime1*1000);
+[r2, x2] = ecdf(runtime2*1000);
+[r3, x3] = ecdf(runtime3*1000);
+[r4, x4] = ecdf(runtime4*1000);
+
+figure(1); hold on;
+plot(x1, r1, '-r', 'linewidth', 2);
+plot(x2, r2, '-b', 'linewidth', 2);
+plot(x3, r3, '-g', 'linewidth', 2);
+plot(x4, r4, '-m', 'linewidth', 2);
+axis([0 1000 0 1]);

### 2013-05-01 src/slave.py
switch to CloudCache mode to deploy

@@ -70,8 +70,8 @@ class SlaveThreadedTcpRequestHandler(SocketServer.BaseRequestHandler):
 		# run the kernel-solver for each task.
 		global DataNodeConnectionPool, ReportCounter, ReportChunk
 		for task in subjob:
-			#solver = kernel.CloudCacheKernel3SAT(task, DataNodeConnectionPool)
-			solver = kernel.BaseKernel3SAT(task, DataNodeConnectionPool)
+			solver = kernel.CloudCacheKernel3SAT(task, DataNodeConnectionPool)
+			#solver = kernel.BaseKernel3SAT(task, DataNodeConnectionPool)
 			__start_timer__ = time.time() # statistics collection.
 			result = solver.solve()
 			__end_timer__ = time.time()

### 2013-05-01 src/configure.py
pipeline feature added

@@ -6,26 +6,20 @@
 	rely on this file to configure the system.
 '''
 
-MASTER_NODE = ['10.215.114.14']
+#MASTER_NODE = ['10.215.114.14']
 #MASTER_NODE = ['domU-12-31-39-06-A8-71.compute-1.internal']
 #MASTER_NODE = ['ec2-54-234-172-153.compute-1.amazonaws.com']
 #MASTER_NODE = ['localhost']
-SLAVE_NODE = ['10.215.197.55', 
-			  '10.200.251.252', 
-			  '10.206.118.135', 
-			  '10.192.169.57']
+#SLAVE_NODE = ['10.215.197.55', '10.200.251.252', '10.206.118.135', '10.192.169.57']
 #SLAVE_NODE = ['domU-12-31-39-10-82-79.compute-1.internal', 'domU-12-31-39-09-CA-D3.compute-1.internal', 'domU-12-31-39-16-26-EF.compute-1.internal', 'domU-12-31-39-16-F6-BD.compute-1.internal']
 #SLAVE_NODE = ['ec2-54-225-2-34.compute-1.amazonaws.com', 'ec2-54-242-129-207.compute-1.amazonaws.com', 'ec2-54-225-22-165.compute-1.amazonaws.com', 'ec2-50-16-144-197.compute-1.amazonaws.com']
 #PRIVATE_TO_PUBLIC_TABLE = {'10.198.129.131':'ec2-54-225-2-34.compute-1.amazonaws.com', '10.210.205.29':'ec2-54-242-129-207.compute-1.amazonaws.com', '10.96.37.25':'ec2-54-225-22-165.compute-1.amazonaws.com', '10.96.245.71':'ec2-50-16-144-197.compute-1.amazonaws.com'}
-#MASTER_NODE = ['192.168.10.144']
-#SLAVE_NODE = ['192.168.10.144'] 
-#SINKER_NODE = ['192.168.10.144']
-#DATA_NODE = ['192.168.10.144']
-DATA_NODE = ['10.215.197.55', 
-			  '10.200.251.252', 
-			  '10.206.118.135', 
-			  '10.192.169.57']
-SINKER_NODE = ['10.248.127.58']
+MASTER_NODE = ['192.168.10.144']
+SLAVE_NODE = ['192.168.10.144'] 
+SINKER_NODE = ['192.168.10.144']
+DATA_NODE = ['192.168.10.144']
[…]

### 2013-05-01 src/kernel.py

@@ -10,6 +10,7 @@
 '''
 import logging
 import tools
+import time
 import csv
 
 
@@ -32,11 +33,11 @@ class BaseKernel3SAT(object):
 	def solve(self):
 		'''public interface for the base kernel-solver.'''
 		solution = self._RecurrsiveSolve(self._Assignment, 0)
-		selector = tools.DataNodeSelector(self._Expression)
-		storageMgr = tools.PersistentStorageManager(self._Pool[selector.getDataNode()])
-		storageMgr.push(self._Expression, solution)
-		logging.info('Solution cached in the Redis ...')
-		return solution
+		#selector = tools.DataNodeSelector(self._Expression)
+		#storageMgr = tools.PersistentStorageManager(self._Pool[selector.getDataNode()])
+		#storageMgr.push(self._Expression, solution)
+		#logging.info('Solution cached in the Redis ...')
+		return (self._Expression, solution)
 
 	def _RecurrsiveSolve(self, assignment, index):
 		'''internal recurrsive solution.'''
@@ -73,19 +74,20 @@ class BaseKernel3SAT(object):
 
 class CloudCacheKernel3SAT(object):
 	'''the cloud cache approach to solve the 3-SAT problem.'''
-	def __init__(self, task, pool):
+	def __init__(self, task, pool, cachehit):
 		self._NumberOfVariable = eval(task.split(',')[0])
 		self._NumberOfExpression = eval(task.split(',')[1])
 		self._Expression = [eval(o) for o in task.split(',')[2:]]
 		self._Assignment = [False for o in range(self._NumberOfVariable)]
 		self._BaseKernel = BaseKernel3SAT(task, pool)
 		self._Pool = pool
+		self._CacheHitStatistics = cachehit
 		logging.info('CloudCacheKernel 3-SAT initialized. n = %d, m = %d', 
 			self._NumberOfVariable, self._NumberOfExpression)
 
 	def solve(self):
 		# setup a statistics for cache hit rate.
-		stat = csv.writer(open(configure.CACHE_STATISTICS_URI, 'a'), delimiter=',')
+		#stat = csv.writer(open(configure.CACHE_STATISTICS_URI, 'a'), delimiter=',')
 		# linear traverse the problem and query the Redis server.
 		for i in range(0, len(self._Expression), 3):
 			subtask = self._Expression[i:]
@@ -94,15 +96,15 @@ class CloudCacheKernel3SAT(object):
 			assignment = storageMgr.query(subtask)
 			if assignment == []:
[…]

### 2013-05-01 src/slave.py

@@ -37,20 +37,24 @@ logging.basicConfig(format=FORMAT, level=logging.DEBUG)
 
 # statistics collection.
 runtime = csv.writer(open(configure.RUNTIME_COLLECTION_URI, 'a'), delimiter=',')
+cachehit = csv.writer(open(configure.CACHE_STATISTICS_URI, 'a'), delimiter=',')
 
 
 # global variable
 DataNodeConnectionPool = {}
+DataNodeConnectionPipeline = {}
 ReportChunk = ''
 ReportCounter = 0
 
 
 # global initialization
 def GlobalInitialization():
-	global DataNodeConnectionPool
+	global DataNodeConnectionPool, DataNodeConnectionPipeline
 	for node in configure.DATA_NODE:
 		DataNodeConnectionPool[node] = redis.ConnectionPool(host=node)
-		logging.info('Estabilished Redis connection: %s', node)
+		DataNodeConnectionPipeline[node] = tools.PipelineStorageManager(
+			redis.Redis(connection_pool=DataNodeConnectionPool[node]))
+		logging.info('Estabilished Redis connection and pipeline: %s', node)
 
 
 class SlaveThreadedTcpRequestHandler(SocketServer.BaseRequestHandler):
@@ -68,15 +72,25 @@ class SlaveThreadedTcpRequestHandler(SocketServer.BaseRequestHandler):
 		logging.info('Job has been received ...')
 		subjob = simplejson.loads(message)
 		# run the kernel-solver for each task.
-		global DataNodeConnectionPool, ReportCounter, ReportChunk
+		global DataNodeConnectionPool, ReportCounter, ReportChunk, DataNodeConnectionPipeline
 		for task in subjob:
-			solver = kernel.CloudCacheKernel3SAT(task, DataNodeConnectionPool)
+			solver = kernel.CloudCacheKernel3SAT(task, DataNodeConnectionPool, cachehit)
+			
 			#solver = kernel.BaseKernel3SAT(task, DataNodeConnectionPool)
 			__start_timer__ = time.time() # statistics collection.
-			result = solver.solve()
+			(problem, result) = solver.solve()
 			__end_timer__ = time.time()
+			
+			# pipeline the cache write.
+			selector = tools.DataNodeSelector(problem)
+			datanode = selector.getDataNode()
+			DataNodeConnectionPipeline[datanode].buffer(problem, result)
[…]

### 2013-05-01 src/tools.py

@@ -195,3 +195,32 @@ class PersistentStorageManager(object):
 			self._RedisConnector.delete(key)
 			count += 1
 		logging.info('%d keys have been clearup in Redis ...', count)
+
+
+class PipelineStorageManager(object):
+	'''the Data Node pipeline cache write class.'''
+	def __init__(self, pipeline):
+		self._DataNodePipeline = pipeline
+		self._BufferSize = 0
+
+	def buffer(self, key, value):
+		key = self._serializeArray(key)
+		value = self._serializeArray(value)
+		self._DataNodePipeline.set(key, value)
+		self._BufferSize += 1
+
+	def getBufferSize(self):
+		return self._BufferSize
+
+	def execute(self):
+		self._DataNodePipeline.execute()
+		self._BufferSize = 0
+	
+	def _serializeArray(self, array):
+		if len(array) == 0:
+			return ''
+		sequence = ''
+		for item in array:
+			sequence += str(item) + ','
+		return sequence[0:len(sequence)-1]
+	

### 2013-05-01 src/configure.py
ready to test cache-feature on EC2 with pipeline

@@ -6,20 +6,20 @@
 	rely on this file to configure the system.
 '''
 
-#MASTER_NODE = ['10.215.114.14']
+MASTER_NODE = ['10.215.114.14']
 #MASTER_NODE = ['domU-12-31-39-06-A8-71.compute-1.internal']
 #MASTER_NODE = ['ec2-54-234-172-153.compute-1.amazonaws.com']
 #MASTER_NODE = ['localhost']
-#SLAVE_NODE = ['10.215.197.55', '10.200.251.252', '10.206.118.135', '10.192.169.57']
+SLAVE_NODE = ['10.215.197.55', '10.200.251.252', '10.206.118.135', '10.192.169.57']
 #SLAVE_NODE = ['domU-12-31-39-10-82-79.compute-1.internal', 'domU-12-31-39-09-CA-D3.compute-1.internal', 'domU-12-31-39-16-26-EF.compute-1.internal', 'domU-12-31-39-16-F6-BD.compute-1.internal']
 #SLAVE_NODE = ['ec2-54-225-2-34.compute-1.amazonaws.com', 'ec2-54-242-129-207.compute-1.amazonaws.com', 'ec2-54-225-22-165.compute-1.amazonaws.com', 'ec2-50-16-144-197.compute-1.amazonaws.com']
 #PRIVATE_TO_PUBLIC_TABLE = {'10.198.129.131':'ec2-54-225-2-34.compute-1.amazonaws.com', '10.210.205.29':'ec2-54-242-129-207.compute-1.amazonaws.com', '10.96.37.25':'ec2-54-225-22-165.compute-1.amazonaws.com', '10.96.245.71':'ec2-50-16-144-197.compute-1.amazonaws.com'}
-MASTER_NODE = ['192.168.10.144']
-SLAVE_NODE = ['192.168.10.144'] 
-SINKER_NODE = ['192.168.10.144']
-DATA_NODE = ['192.168.10.144']
-#DATA_NODE = ['10.215.197.55', '10.200.251.252', '10.206.118.135', '10.192.169.57']
-#SINKER_NODE = ['10.248.127.58']
+#MASTER_NODE = ['192.168.10.144']
+#SLAVE_NODE = ['192.168.10.144'] 
+#SINKER_NODE = ['192.168.10.144']
+#DATA_NODE = ['192.168.10.144']
[…]

### 2013-05-01 src/external/3-sat-data.cc
new data generator

@@ -19,16 +19,19 @@
 
 using namespace std;
 
+const int MAX_NUMBER_VARIABLE = 16;
+const int MAX_NUMBER_EXPRESSION = 256;
+
 
 int main (int argc, char *argv[]) {
-	int NumberOfCases = 100;
+	int NumberOfCases = 10000;
 	if (argc == 3 && strcmp(argv[1], "-n") == 0)
 		NumberOfCases = atoi(argv[2]);
 	FILE *fp = fopen("3-sat.in", "w");
 	srand(time(NULL));
 	for (int i = 0; i < NumberOfCases; ++i) {
-		int NumberOfVariables = rand() % 20 + 1;
-		int NumberOfExpressions = 3 * (rand() % 30 + 1);
+		int NumberOfVariables = rand() % MAX_NUMBER_VARIABLE + 1;
+		int NumberOfExpressions = 3 * (rand() % MAX_NUMBER_EXPRESSION + 1);
 		fprintf(fp, "%d,%d", NumberOfVariables, NumberOfExpressions);
 		for (int j = 0; j < NumberOfExpressions; ++j) {
 			int x = (rand() % 100000) % NumberOfVariables;

### 2013-05-01 src/redis-clean.py
add redis-clean.py

@@ -1,0 +1,10 @@
+import redis
+
+connection = redis.Redis()
+pipe = connection.pipeline()
+
+for key in connection.keys():
+	pipe.delete(key)
+
+pipe.execute()
+

### 2013-05-01 src/slave.py
ready to deploy to test base-kernel

@@ -74,22 +74,20 @@ class SlaveThreadedTcpRequestHandler(SocketServer.BaseRequestHandler):
 		# run the kernel-solver for each task.
 		global DataNodeConnectionPool, ReportCounter, ReportChunk, DataNodeConnectionPipeline
 		for task in subjob:
-			solver = kernel.CloudCacheKernel3SAT(task, DataNodeConnectionPool, cachehit)
-			
-			#solver = kernel.BaseKernel3SAT(task, DataNodeConnectionPool)
+			#solver = kernel.CloudCacheKernel3SAT(task, DataNodeConnectionPool, cachehit)
+			solver = kernel.BaseKernel3SAT(task, DataNodeConnectionPool)
 			__start_timer__ = time.time() # statistics collection.
 			(problem, result) = solver.solve()
 			__end_timer__ = time.time()
-			
-			# pipeline the cache write.
-			selector = tools.DataNodeSelector(problem)
-			datanode = selector.getDataNode()
-			DataNodeConnectionPipeline[datanode].buffer(problem, result)
-			if DataNodeConnectionPipeline[datanode].getBufferSize == configure.PIPELINE_BUFFER_SIZE:
-				DataNodeConnectionPipeline[datanode].execute()
-
 			logging.info('Task finished, cost = %f ...', __end_timer__ - __start_timer__)
 			runtime.writerow([__end_timer__, __start_timer__])
+			
+			# pipeline the cache write.
+			#selector = tools.DataNodeSelector(problem)
+			#datanode = selector.getDataNode()
+			#DataNodeConnectionPipeline[datanode].buffer(problem, result)
+			#if DataNodeConnectionPipeline[datanode].getBufferSize == configure.PIPELINE_BUFFER_SIZE:
+			#	DataNodeConnectionPipeline[datanode].execute()
 			
 			# report the results.
 			reporter = tools.TaskReporter()

### 2013-05-02 paper/tex/performance.tex
experiment done.

@@
 
-Additionally, we run a standard benchmark for Redis server on the Data Node. The results are shown in Table~\ref{}.
+Additionally, we run a standard benchmark for Redis server on the Data Node.
+The results are shown in Table~\ref{tab:redis}.
+Two operations \emph{GET} and \emph{SET} are frequently used in CloudCache, which has $25316.46$ and $17421.60$ throughput respectively.
+
+\begin{table}
+\centering
+\caption{Redis Server Benchmark}
+\begin{tabular}{ll}\toprule
+Redis Operations & Benchmark Results \\\midrule
+PING & 26109.66 requests per second \\
+MSET & 12406.95 requests per second \\
+SET & 17421.60 requests per second \\
+GET & 25316.46 requests per second \\
+INCR & 24813.90 requests per second \\
+LPUSH & 27700.83 requests per second \\
+LPOP & 28169.02 requests per second \\
+SADD & 28169.02 requests per second \\
+SPOP & 27777.78 requests per second \\
+LPUSH & 27855.15 requests per second \\
+LRANGE & 3373.82 requests per second \\\bottomrule
+\end{tabular}
+\label{tab:redis}
+\end{table}
 

### 2013-05-02 paper/data/runtime_analysis.m

@@ -1,23 +1,51 @@
 clear all;
-slave1 = load('stat_slave_1.out');
-slave2 = load('stat_slave_2.out');
-slave3 = load('stat_slave_3.out');
-slave4 = load('stat_slave_4.out');
+slave1 = load('simple/stat_slave_1_1.out');
+slave2 = load('simple/stat_slave_2_1.out');
+slave3 = load('simple/stat_slave_3_1.out');
+slave4 = load('simple/stat_slave_4_1.out');
+simple = [slave1(2500:length(slave1),:); 
+          slave2(2500:length(slave2),:); 
+          slave3(2500:length(slave3),:); 
+          slave4(2500:length(slave4),:)];
+runtime1 = simple(:,1) - simple(:,2);
 
-runtime1 = slave1(:,1) - slave1(:,2);
-runtime2 = slave2(:,1) - slave2(:,2);
-runtime3 = slave3(:,1) - slave3(:,2);
-runtime4 = slave4(:,1) - slave4(:,2);
+slave1 = load('cloud-cache/stat_slave_1_1.out');
+slave2 = load('cloud-cache/stat_slave_2_1.out');
+slave3 = load('cloud-cache/stat_slave_3_1.out');
+slave4 = load('cloud-cache/stat_slave_4_1.out');
+ccache = [slave1; slave2; slave3; slave4];
+runtime2 = ccache(:,1) - ccache(:,2);
 
+[r1, x1] = ecdf(runtime1);
+[r2, x2] = ecdf(runtime2);
 
-[r1, x1] = ecdf(runtime1*1000);
-[r2, x2] = ecdf(runtime2*1000);
-[r3, x3] = ecdf(runtime3*1000);
-[r4, x4] = ecdf(runtime4*1000);
 
 figure(1); hold on;
 plot(x1, r1, '-r', 'linewidth', 2);
 plot(x2, r2, '-b', 'linewidth', 2);
-plot(x3, r3, '-g', 'linewidth', 2);
-plot(x4, r4, '-m', 'linewidth', 2);
-axis([0 1000 0 1]);
+axis([0 10 0 1]);
+grid on;
+hold off;
+
+% slave = sortrows(simple, 1);
+% length(slave)
+% 
+% task = [0];
+% start = 1367334283;
+% k = 1
+% t = 0
+% for i = 1:length(slave)
+%     if slave(i,1) < start + 300
+%         task(k) = task(k) + (slave(i,1) - slave(i,2));
+%         t = t + 1;
+%     else
[…]

### 2013-05-02 paper/data/simple/retrieve.sh

@@ -1,0 +1,11 @@
+scp -i ~/.ec2/amazon-ubuntu.pem ubuntu@ec2-54-224-241-85.compute-1.amazonaws.com:/home/ubuntu/cloud-cache/src/external/stat.out stat_slave_1_1.out
+scp -i ~/.ec2/amazon-ubuntu.pem ubuntu@ec2-54-224-241-85.compute-1.amazonaws.com:/home/ubuntu/cloud-cache/src/external/cache.out cache_slave_1_1.out
+
+scp -i ~/.ec2/amazon-ubuntu.pem ubuntu@ec2-54-225-29-78.compute-1.amazonaws.com:/home/ubuntu/cloud-cache/src/external/stat.out stat_slave_2_1.out
+scp -i ~/.ec2/amazon-ubuntu.pem ubuntu@ec2-54-225-29-78.compute-1.amazonaws.com:/home/ubuntu/cloud-cache/src/external/cache.out cache_slave_2_1.out
+
+scp -i ~/.ec2/amazon-ubuntu.pem ubuntu@ec2-54-224-234-78.compute-1.amazonaws.com:/home/ubuntu/cloud-cache/src/external/stat.out stat_slave_3_1.out
+scp -i ~/.ec2/amazon-ubuntu.pem ubuntu@ec2-54-224-234-78.compute-1.amazonaws.com:/home/ubuntu/cloud-cache/src/external/cache.out cache_slave_3_1.out
+
+scp -i ~/.ec2/amazon-ubuntu.pem ubuntu@ec2-54-243-6-222.compute-1.amazonaws.com:/home/ubuntu/cloud-cache/src/external/stat.out stat_slave_4_1.out
+scp -i ~/.ec2/amazon-ubuntu.pem ubuntu@ec2-54-243-6-222.compute-1.amazonaws.com:/home/ubuntu/cloud-cache/src/external/cache.out cache_slave_4_1.out

### 2013-05-03 paper/tex/conclusion.tex
finish the paper

\section{Conclusion}\label{sec:conclusion}
In this document, we describe the design and implementation of CloudCache framework. Through the evaluation, we find that the advantages of CloudCache framework has larger margin for the hard solving problem instances. We also look into the generalness of the framework by designing the solutions for the \emph{k-coloring} problem in the graph. The the solution paradigm fits into the problem very well, which reinforce the advantages of CloudCache framework. Finally, the system performance in CPU and network-in/out evaluation provides us a good fingerprints of the CloudCache framework as a whole.

### 2013-05-03 paper/tex/design.tex
finish the paper

@@
 In addition to cache the problem's solution, the solution needs to report to the Sink Node where the client program will come and retrieve the final results for all tasks in the job after the system finish the job.
-Note that we only have single Sink Node while the each kernel-solver will report its results to the Sink Node, the pressure at the Sink Node is significant which defects the whole system's throughput.
-Therefore, we have a solution accumulator attached to each Slave Node.
-The solution will be accumulated into a certain amount, then the Slave Node will report the results once.
+Note that we only have single Sink Node while the each kernel-solver will report its results to the Sink Node, the load at the Sink Node is significant which defects the whole system's throughput.
+Therefore, we have a small optimization that buffers the solution in each Slave Node until certain amount, then the Slave Node will report the buffered results together at once.
 
 \subsection{Framework Generalness}
-An expected design goal of CloudCache is the generalness, we want to make this framework to be an proper and simply approach to solve many different types of hard problems in the cloud.
+An expected design goal of CloudCache is the generalness, we want to make this framework to be a proper and simple approach to solve many different types of hard problems in the cloud.
 According to the design, only two things need to be defined by the developer before using the framework.
@@
 Then the framework will start executing the batch job.
-In this section, we will show three hard problems' solution using CloudCache's framework.
+In this section, we will show two hard problems' solution using CloudCache framework.
 

### 2013-05-03 paper/tex/implementation.tex
framework performance
experiment done.
finish the paper

@@
 \subsection{Software Architecture}
-We use Python as the language to implement the system. It consists of seven major modules in the source code.
+We use Python as the language to implement the system. It consists of seven major modules in the source code\footnote{Source code is hosted on Github: https://github.com/little-eyes/cloud-cache.git}.
 
@@
 Again, the developer does not need to pay additional attention to the data structure of key and value, because the two APIs above will serialize the key and value first before conducting cache operations.
+
+\subsection{Implementation Optimizations}
+After we implement the first version, we do not find too much advantages of the CloudCache framework.
+Thereafter, we analyze the code we write, and we realize the interaction between the Slave Node and Data Node are too frequent during the problem solving phase, which is reaching the benchmark upper bound of the Data Node.
+Each query and push operations costs more time than it should be.
+Therefore, we use a pipeline technique to solve the problem.
+Every time the problem is fully solved, either through cache query or brute-force, we put the result key-value pair into a pipeline.
+When the pipeline has certain number of solutions need to be cached in the cloud, we execute the whole pipeline once.
+This brings a decent performance gain for the CloudCache framework.

### 2013-05-03 paper/tex/performance.tex
finish the paper

@@
 \subsection{Problem Solving Performance}
+One of the major performance metrics is the problem solving time, which shows how much time to solve a problem using CloudCache framework.
+In this evaluation, we generate $1,000,000$ problem instances randomly whose number of variables is between $1$ and $20$ and the number of clauses is between $1$ and $256$.
+We solve the $1,000,000$ twice: the first time we use brute-force approach by exhaustive search, and the second time we solve it within the CloudCache framework.
+During the experiments, we collect the time of each problem instance, then we draw a cumulative distribution frequency curve in Fig.~\ref{fig:time}.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.45\textwidth]{pics/time.pdf}
+\caption{The problem solving time CDF curve.}
+\label{fig:time}
+\end{figure}
+
+As is shown in the figure, for easy problem instances, which usually can be  solved within a second, brute-force approach has more advantages.
+However, brute-force approach cannot benefit the hard problem instances at all, while the CloudCache framework can handle it very well.
+We think the linear scan and cache query process cost non-trivial amount of time for easy problem instances, but this time benefits the hard problem instances by reducing the exhaustive search into a simple validation process.
+Finally, it is safe to say the CloudCache framework is a good fit for the hard problem instances.
 
@@
 
-\begin{figure*}[!htb]
+\begin{figure*}
 \minipage{0.33\textwidth}

### 2013-05-03 paper/data/runtime_analysis.m

@@ -23,8 +23,12 @@ runtime2 = ccache(:,1) - ccache(:,2);
 figure(1); hold on;
 plot(x1, r1, '-r', 'linewidth', 2);
 plot(x2, r2, '-b', 'linewidth', 2);
-axis([0 10 0 1]);
+axis([0 5 0 1]);
 grid on;
+set(gca, 'fontsize', 14);
+xlabel('Problem Solving Time (second)');
+ylabel('CDF');
+legend('Brute-force solution', 'CloudCache Framework');
 hold off;
 
 % slave = sortrows(simple, 1);

### 2013-05-03 src/kernel.py
code comments revise.

@@ -86,6 +86,7 @@ class CloudCacheKernel3SAT(object):
 			self._NumberOfVariable, self._NumberOfExpression)
 
 	def solve(self):
+		'''the public solve API.'''
 		# setup a statistics for cache hit rate.
 		#stat = csv.writer(open(configure.CACHE_STATISTICS_URI, 'a'), delimiter=',')
 		# linear traverse the problem and query the Redis server.

### 2013-05-03 src/sinker.py

@@ -2,7 +2,7 @@
 	CS594 Cloud Computing Course Project.
 	Author: Jilong Liao (jliao2@utk.edu)
 
-	The Sink Node is used to receive all the solutions comes out
+	The Sinker Node is used to receive all the solutions comes out
 	of the Slave Node which is isolated from the Master Node.
 
 	The change of the design comes from a benchmark which indicates

### 2013-05-03 src/slave.py

@@ -74,8 +74,8 @@ class SlaveThreadedTcpRequestHandler(SocketServer.BaseRequestHandler):
 		# run the kernel-solver for each task.
 		global DataNodeConnectionPool, ReportCounter, ReportChunk, DataNodeConnectionPipeline
 		for task in subjob:
-			#solver = kernel.CloudCacheKernel3SAT(task, DataNodeConnectionPool, cachehit)
-			solver = kernel.BaseKernel3SAT(task, DataNodeConnectionPool)
+			solver = kernel.CloudCacheKernel3SAT(task, DataNodeConnectionPool, cachehit)
+			#solver = kernel.BaseKernel3SAT(task, DataNodeConnectionPool)
 			__start_timer__ = time.time() # statistics collection.
 			(problem, result) = solver.solve()
 			__end_timer__ = time.time()
@@ -83,11 +83,11 @@ class SlaveThreadedTcpRequestHandler(SocketServer.BaseRequestHandler):
 			runtime.writerow([__end_timer__, __start_timer__])
 			
 			# pipeline the cache write.
-			#selector = tools.DataNodeSelector(problem)
-			#datanode = selector.getDataNode()
-			#DataNodeConnectionPipeline[datanode].buffer(problem, result)
-			#if DataNodeConnectionPipeline[datanode].getBufferSize == configure.PIPELINE_BUFFER_SIZE:
-			#	DataNodeConnectionPipeline[datanode].execute()
+			selector = tools.DataNodeSelector(problem)
+			datanode = selector.getDataNode()
+			DataNodeConnectionPipeline[datanode].buffer(problem, result)
+			if DataNodeConnectionPipeline[datanode].getBufferSize == configure.PIPELINE_BUFFER_SIZE:
+				DataNodeConnectionPipeline[datanode].execute()
 			
 			# report the results.
 			reporter = tools.TaskReporter()

### 2013-05-03 src/tools.py

@@ -49,6 +49,7 @@ class SlaveNodeSelector(object):
 		self._SlaveNodeCheckinTable = checkin
 	
 	def select(self):
+		'''select a Slave Node to assign the task.'''
 		EarliestCheckin = None
 		SelectedSlave = configure.SLAVE_STATUS_NOT_AVAILABLE
 		for slave in self._SlaveNodeStatusTable.keys():
@@ -58,6 +59,7 @@ class SlaveNodeSelector(object):
 		return SelectedSlave
 	
 	def random(self):
+		'''if multiple Slave Nodes are available, randomly choose one.'''
 		return random.choice(self._SlaveNodeStatusTable.keys())
 
 
@@ -92,10 +94,12 @@ class TaskReporter(object):
 		return simplejson.dumps({'task':task, 'result':result})
 
 	def combine(self, chunk, task, result):
+		'''accumualte the reports together.'''
 		report = self._serializeReport(task, result)
 		return chunk + report + '\n'	
 
 	def report(self, report):
+		'''report the results to Sinker Node.'''
 		sendSocket = socket.socket(socket.AF_INET, socket.SOCK_STREAM)
 		sendSocket.connect((self._Ip, self._Port))
 		try:
@@ -116,6 +120,7 @@ class LocalNetworkManager(object):
 		return IpAddress
 	
 	def probeHost(self, host, port):
+		'''probe a host is online or not, used to check Slave Node's status.'''
 		probeSocket = socket.socket(socket.AF_INET, socket.SOCK_DGRAM)
 		probeSocket.settimeout(1.0) # timeout is set to be 1 second.
 		probeSocket.connect((host, port))
@@ -136,6 +141,7 @@ class DataNodeSelector(object):
 		self._Task = self._serializeArray(task)
 
 	def getDataNode(self):
+		'''use hash to select the Data Node.'''
 		return configure.DATA_NODE[self._simpleHash(self._Task)]
 	
 	def _simpleHash(self, string):
@@ -204,6 +210,7 @@ class PipelineStorageManager(object):
 		self._BufferSize = 0
 
 	def buffer(self, key, value):
+		'''buffer the push oepration.'''
 		key = self._serializeArray(key)
 		value = self._serializeArray(value)
 		self._DataNodePipeline.set(key, value)
@@ -213,6 +220,7 @@ class PipelineStorageManager(object):
 		return self._BufferSize
 
 	def execute(self):
[…]

### 2013-05-03 paper/tex/conclusion.tex
paper revision extra.

@@
 In this document, we describe the design and implementation of CloudCache framework.
-Through the evaluation, we find that the advantages of CloudCache framework has larger margin for the hard solving problem instances.
+Through the evaluation, we find that the advantages of CloudCache framework has larger margin to solve harder problem instances.
 We also look into the generalness of the framework by designing the solutions for the \emph{k-coloring} problem in the graph.
-The the solution paradigm fits into the problem very well, which reinforce the advantages of CloudCache framework.
+The the solution paradigm fits into the problem very well, which reinforces the advantages of CloudCache framework.
 Finally, the system performance in CPU and network-in/out evaluation provides us a good fingerprints of the CloudCache framework as a whole.

### 2013-05-04 essay/main.tex
write essay

@@
-\documentclass[11pt, times]{article}
+\documentclass[11pt, journal, onecolumn]{IEEEtran}
 \usepackage{cite}
+\usepackage{amsmath, amsthm, amsfonts}
 \usepackage[top=1in, bottom=0.75in, left=0.75in, right=0.75in]{geometry}
-%\usepackage{pslatex}
 
@@
 Major cloud computing vendors, like Amazon, Google and Dropbox, have provided users and businesses many advantages such as reliable and convenient storage, elastic computing power, and simple application deployment, lower IT infrastructure cost, etc.
-In $10$ years, I will expect cloud computing's influence far beyond the current achievements, but deeply inside mobile technology, scientific computing, massive online education and online-to-offline market.
+In $10$ years, I will expect cloud computing's influence far beyond the current achievements, but deeply inside mobile technology, massive open online education, online-to-offline business and scientific computing.
 In this essay, I will discuss this point with my observations and understandings.

### 2013-05-04 essay/tex/essay.tex
write essay

@@
 \section{Introduction}
+In recent years, cloud computing has provided us with a lot of benefits in many area.
+Major cloud computing vendors like Amazon, Google and Dropbox have offered the users around the world a cheap, convenient and secure computing and storage resource.
+For example, Amazon EC2 is one of the most popular cloud computing platform for many companies and individuals.
+The various types of virtual instances at different price strategies provide very flexible choices for the users.
+I rent a \emph{m1.micro} instance for the use of my person website and blog for three years at a decent price around $100$ dollas.
+With the virtual instance, I do not need to install a physical machine at my home and maintain it day by day, which definitely costs more than $100$ dollas for three years.
 
-\section{Mobile Computing and Cloud Computing}
+An additional example of another scenario of cloud computing's application could be cloud storage.
+Either Dropbox or Google Drive or Amazon Cloud Storage, they provide both companies and individuals cheap and convenient cloud storage which we do not need to worry about the data loss or accessibility.
+Even though three of them have different data privacy terms, people still quite enjoy this type of services.
+For example, Dropbox has a marketing plan for university students who has a \emph{.edu} email will obtain an extra $3$GB plus his own $2$GB storage space for free.
+When I look around with other students, most of them seems to be very happy with the current services.
+They use Dropbox as a USB drive to share or transfer large amount of data over the air; they also use Dropbox to show pictures or documents during their presentation.
+Thus, it seeems that the free $5$GB \emph{USB-air-drive} could become more popular and convenient than a $\$10$-$\$15$ USB flash drive.
+
+\section{Mobile and Cloud Computing}
 

### 2013-05-04 paper/tex/design.tex

@@
 \subsection{The Problem-Solution Abstraction}
-Many different types of hard problem we encounter have various input structure.
-For instance, 3-SAT problem input a logic expression while Clique problem needs a graph structure.
-Those different types of inputs brings the challenges to the CloudCache framework, because it is possible the CloudCache framework host many different types of problems and solutions and the cache query operation need to find the exact solutions for a certain problem.
-If we do not have a uniform structure for the all problems, the complexity in localizing problems and its solutions will be very large.
+Many different types of hard problem we encounter have various input structures.
+For instance, 3-SAT problem inputs a logic expression while Clique problem needs a graph structure.
+Those different types of inputs bring the challenge to the CloudCache framework, because it is possible the CloudCache framework hosts many different types of problems and solutions and the cache query operations need to find the exact solutions for a certain problem.
+If we do not have a uniform structure for all problems, the complexity in localizing problems and its solutions will be very large.
 
@@
 \centering
-\includegraphics[width=0.5\textwidth]{pics/workflow.pdf}
+\includegraphics[width=0.45\textwidth]{pics/workflow.pdf}
 \caption{The Logic Diagram of CloudCache}
@@
 The CloudCache framework (Fig.~\ref{fig:logic}) includes four types of nodes and three computation phases in the cloud infrastructure.
-The nodes are \emph{Master Node}, \emph{Slave Node}, \emph{Data Node} and \emph{Sink Node}; the three phases are \emph{Job Distribution Phase}, \emph{Task Solve Phase} and \emph{Solution Sink Phase}.
+The nodes are \emph{Master Node}, \emph{Slave Node}, \emph{Data Node} and \emph{Sinker Node}; the three phases are \emph{Job Distribution Phase}, \emph{Task Solve Phase} and \emph{Solution Sink Phase}.
 In addition, the \emph{Client Problem} exists outside of the cloud infrastructure which needs to be submitted into the CloudCache framework.
@@
 
-Whether the kernel-solver find the existing solutions or solve it by itself, the solution for the assigned problem will be cached in the Data Node, selected by the same hash function.
-We use a hash function to shard the queries because we consider the load balance of the Data Node which is much busier than Slave Node or Master Node in the system.
-In addition to cache the problem's solution, the solution needs to report to the Sink Node where the client program will come and retrieve the final results for all tasks in the job after the system finish the job.
-Note that we only have single Sink Node while the each kernel-solver will report its results to the Sink Node, the load at the Sink Node is significant which defects the whole system's throughput.
+Whether the kernel-solver find the existing solutions or solve it by itself, the solution for the assigned problem will be cached in the Data Node selected by the same hash function.
+We use a hash function to shard the queries because we consider the load balance of the Data Node, which is much busier than Slave Node or Master Node in the system.
+In addition to cache the problem's solution, the solution needs to report to the Sinker Node where the client program will come and retrieve the final results for all tasks in the job after the system finishes the job.
+Note that we only have single Sinker Node while the each kernel-solver will report its results to the Sinker Node, the load at the Sinker Node is significant which defects the whole system's throughput.
 Therefore, we have a small optimization that buffers the solution in each Slave Node until certain amount, then the Slave Node will report the buffered results together at once.
@@
 First, the problem and solution's data structure; second, the kernel-solver of the problem, namely when to query the cache and when to solve the problem by itself.
-After finishing the two parts, the developer can submit a batch of problem as a job to the Master Node, where each problem is regarded as a task.
+After finishing the two parts, the developer can submit a batch of problems as a job to the Master Node, where each problem is regarded as a task.
 Then the framework will start executing the batch job.
-In this section, we will show two hard problems' solution using CloudCache framework.
+In this section, we will show two hard problems' solutions using CloudCache framework.
 
@@
 For this problem, we use the expression vector as the key, but the vector is in a specific format.
-The boolean variable's index represents the variable itself in the vector, and the the index is set to be negative is the boolean variable has a ``not'' operator.
-The elements in expression are separated by a comma.
+The boolean variable's index represents the variable itself in the vector, and the the index is set to be negative if the boolean variable has a ``not'' operator.
 Therefore, the \emph{key} for Eq.~\ref{eq:3-sat} is $[1,2,-3,2,3,4,3,-4,5]$.
@@
 The kernel-solver has two stages, the first stage is to check if the expression or any subexpression has been solved.
-We use a linear scan to do it by moving the head clause and check the subexpression between the head clause and the end one.
+We use a linear scan to do it by traversing from the head clause and check the subexpression between the head clause and the end one.
 For the example in Eq.~\ref{eq:3-sat}, we will check Eq.~\ref{eq:3-sat1},~\ref{eq:3-sat2},~\ref{eq:3-sat3}.
@@
 Similarly, we first need to abstract the problem-solution pairs.
-For the problem, we use a matrix $\mathbf{R}_{n\times n}$ to represent the graph which is the \emph{key}, and the \emph{value} is the color assignment vector $\mathbf{a} = [a_1, a_2, ..., a_n]$ where $n$ is the number of vertex in the graph.
+For this problem, we use a matrix $\mathbf{R}_{n\times n}$ to represent the graph which is the \emph{key}, and the \emph{value} is the color assignment vector $\mathbf{a} = [a_1, a_2, ..., a_n]$ where $n$ is the number of vertex in the graph.
 
-The kernel-solver is also using a linear scan to all the vertices.
+The kernel-solver also uses a linear scan to all the vertices.
 For each vertex, we remove the edges connected to the vertex, then we have a new adjacent matrix $\hat{\mathbf{R}}_{(n-1)\times (n-1)}$ which is actually a subgraph of the original one.
 For this subgraph, we query the CloudCache to retrieve the existing color assignment.
-If success, we need to validate the assignment by enumerating the color of the removed vertex combining with the existing solution to see if the complete assignment can fit into the original graph.
-If so, we can cache the solution; if not, we continue removing another vertex in $\mathbf{R}_{n\times n}$ until we scan all the vertices one time.
-If cache is not working at all, the brute-force solver is triggered.
+If success, we need to validate the assignment by enumerating the color of the removed vertex and combining with the existing solution to see if the complete assignment can fit into the original graph.
+If so, we can cache the solution; if not, we continue removing another vertex in $\mathbf{R}_{n\times n}$ until we scan all the vertices.
+If cache is not working at all, the brute-force solver otherwise is triggered.

### 2013-05-04 paper/tex/implementation.tex

@@
 \subsection{The CloudCache Infrastructure}
-As is shown in Fig.~\ref{fig:system}, the infrastructure in the cloud consists of four different types of nodes: Master Node, Slave Node, Data Node and Sink Node.
+As is shown in Fig.~\ref{fig:system}, the infrastructure in the cloud consists of four different types of nodes: Master Node, Slave Node, Data Node and Sinker Node.
 Outside of the cloud infrastructure, we have a Client which will submit the job to the Master Node.
-After the job is done, the Sink Node will push the job results to the Client.
+After the job is done, the Sinker Node will push the job results to the Client.
 
@@
 The Slave Node is also a multi-threaded TCP server, but once the Slave Node receives the job distributed from the Master Node, it will fork a worker thread to execute every task in the job.
-We do not fork multiple threads for each task because we do not want the first arrive job's tasks overwhelm the Slave Node (it is possible for Slave Node to run different jobs concurrently).
+We do not fork multiple threads for multiple tasks because we do not want the first arrive job's tasks overwhelm the Slave Node.
 
@@
 
-Finally, the Sink Node is the one to collect all the results and provide the final job result to the Client.
+Finally, the Sinker Node is the one to collect all the results and provide the final job result to the Client.
 To avoid the Slave Node's highly frequent task report, we buffer the report at the Slave Node until the buffer is full.
-This small optimization reduce the load of Sink Node, and increase the Slave Node's efficiency as well (task reporting blocks the Slave Node moving forward).
+This small optimization reduce the load of Sinker Node, and increase the Slave Node's efficiency as well (task reporting blocks the Slave Node moving forward).
 
@@
 \subsection{Software Architecture}
-We use Python as the language to implement the system. It consists of seven major modules in the source code\footnote{Source code is hosted on Github: https://github.com/little-eyes/cloud-cache.git}.
+We use Python to implement the system. The software stack consists of seven major modules in the source code\footnote{Source code is hosted on Github: https://github.com/little-eyes/cloud-cache.git}.
 
@@
 \item slave.py. This module is the component to start a Slave Node. It includes a multi-threaded TCP server as well, and a job execution handler and some statistic variables.
-\item sink.py. The Sink Node module which receives the accumulated task report and dump the solutions to disk. After the job finished, the Client can come to retrieve the results.
+\item sinker.py. The Sinker Node module which receives the accumulated task report and dumps the solutions to disk. After the job finished, the Client can come to retrieve the results.
 \item kernel.py. The core module to kernel-solver. A developer should define a class to solve the problem, then the Slave Node will call the kernel-solver based on the configuration.
 \item tools.py. It defines many helper class to help simplify the architecture like JobDispatcher, etc.
-\item configure.py. The place is used to define any global configuration details, for instance, the Master Node, Slave Node, Data Node and Sink Node.
+\item configure.py. The place is used to define any global configuration details, for instance, the Master Node, Slave Node, Data Node and Sinker Node.
 \end{itemize}
@@
 \subsection{Programming Interface}
-Two important programming interface in the CloudCache is in the tools.py module.
+Two important programming interfaces in the CloudCache is in the tools.py module.
 The two APIs are \emph{tools.PersistentStorageManager.query(key)} and \emph{tools.PersistentStorageManager.push(key, value)}.
@@
 Thereafter, we analyze the code we write, and we realize the interaction between the Slave Node and Data Node are too frequent during the problem solving phase, which is reaching the benchmark upper bound of the Data Node.
-Each query and push operations costs more time than it should be.
+Each query or push operation costs more time than it should be.
 Therefore, we use a pipeline technique to solve the problem.

### 2013-05-04 paper/tex/introduction.tex

@@
 
-By the booming time of cloud computing, people may have the chance to rethink of the way to solve some existing hard problems in computer science.
 The hard problems (usually belongs to the NP-Complete category like 3-SAT) often require exponential computation time to traverse the solution space in a brute-force manner.
-In addition, people may need to solve the same types of problems again and again in different instance.
+In addition, people may need to solve the same types of problems again and again in different instances.
 Some instances or subproblems possibly have been solved by others.
@@
 3-SAT, could have numerous problem instance, which may require several disks to store them, let alone we have many different types of hard problems.
-Cloud computing, at this point, could be a proper plagiarism because it is much less expensive to build a large scale storage and its management system.
-The other challenge is how we abstract the hard problems in a way that the platform we build could be more general to many different type of hard problems.
+Cloud computing, at this point, could be a proper paradigm because it is much less expensive to build a large scale storage and its management system.
+The other challenge is how we abstract the hard problems in a way that the platform we build could be more general to many different types of hard problems.
 
 In this document, we propose \emph{CloudCache} framework which is built on top of general cloud computing platform and provides the interface to query, cache and solve hard problems in an easier way.
-The CloudCache framework abstracts the \emph{problem-solution} pair into \emph{key-value} objects, and uses some object storage system to cache existing problems and solutions.
+The CloudCache framework abstracts the \emph{problem-solution} pairs into \emph{key-value} objects, and uses some object storage system to cache existing problems and solutions.
 Further, the CloudCache framework provides a general problem solving interface \emph{kernel-solver}, so that the developer can easily write a problem's solution and solve it within the CloudCache's framework.

### 2013-05-04 paper/tex/performance.tex

@@
 To evaluate the performance of the CloudCache and validate whether the cache idea is feasible in reality, we deploy the CloudCache framework to Amazon EC2 platform in a small scale (Fig.~\ref{fig:ec2}).
-In the deployment, there are $1$ Master Node, $4$ Slave Node/Data Node, and $1$ Sink Node.
-All EC2 instance are micro which have the specifications in Table~\ref{tab:ec2}.
+In the deployment, there are $1$ Master Node, $4$ Slave Node/Data Node, and $1$ Sinker Node.
+All EC2 instances are micro which have the specifications in Table~\ref{tab:ec2}.
 
@@
 The results are shown in Table~\ref{tab:redis}.
-Two operations \emph{GET} and \emph{SET} are frequently used in CloudCache, which has $25316.46$ and $17421.60$ throughput respectively.
+Two operations \emph{GET} and \emph{SET} are frequently used in CloudCache, which has the throughput of $25316.46$ and $17421.60$ requests per second respectively.
 
@@
 Then we randomly generate $1,000,000$ 3-SAT problem instances, then the Client node submit those problem instances as a job to the Master Node.
-The Slave Node start solving the problem using kernel-solver and we collect the runtime statistics for the problem solving time and cache hit rate.
+The Slave Node starts solving the problem using kernel-solver and we collect the runtime statistics for the problem solving time and cache hit rate.
 Further, we use the Amazon CloudWatch as the system performance monitor tool to track the CPU usage and network consumption inside the framework.
@@
 During the next several hours, the Slave Node is busy solving problem assigned to itself.
-From Fig.~\ref{fig:slave_in} we can see the job receiving's in-network fringerprints.
-Once the Slave Node starts working, the out-network starts increase because the generated solutions will be sinked to the Sink Node.
+From Fig.~\ref{fig:slave_in} we can see the job receiving phase's in-network fringerprints.
+Once the Slave Node starts working, the out-network starts increasing because the generated solutions will be sinked to the Sinker Node.
 Thus, as is illustrated in Fig.~\ref{fig:slave_out}, the out-network starts busy right after the Slave Node starts working.
@@
 Finally, the Sinker Node's CPU (Fig.~\ref{fig:sinker_cpu}) is in mild load because we adopt the solution report buffer in the Slave Node.
-The in-network (Fig.~\ref{fig:sinker_in}) confirms the conclusions that the framework is speeding up the problem solution as a whole, because the increase in the in-network has the same grow style with Slave Node's out-network.
-The Sinker Node's out-network (Fig.~\ref{fig:sinker_out}) also shows the ACKs for receiving data from TCP which has the similar shape with the in-network.
+The in-network (Fig.~\ref{fig:sinker_in}) confirms the conclusions that the framework is speeding up the problem solution as a whole, because the increase in the in-network has the same growing style with Slave Node's out-network.
+The Sinker Node's out-network (Fig.~\ref{fig:sinker_out}) also shows the ACKs for receiving data from TCP which has the similar shape to the in-network.
 

### 2013-05-04 essay/tex/essay.tex
write education part one.

@@
 With the virtual instance, I do not need to install a physical machine at my home and maintain it day by day, which definitely costs more than $100$ dollas for three years.
+Besides individual users like me, many companies either big ones like Netflix or startups like Pinterest choose Amazon AWS as their dedicated IT infrastructure to reduce the cost of maintaining a complete IT infrastructure by themselves.
 
@@
 They use Dropbox as a USB drive to share or transfer large amount of data over the air; they also use Dropbox to show pictures or documents during their presentation.
-Thus, it seeems that the free $5$GB \emph{USB-air-drive} could become more popular and convenient than a $\$10$-$\$15$ USB flash drive.
+Thus, it seeems that the free $5$GB \emph{USB-air-drive} (which I called for Dropbox) could become more popular and convenient than a $\$10$-$\$15$ USB flash drive.
+
+Event if cloud computing had achieved so many advantages all over these years, we may notice that the current stage of cloud computing has influenced very limited industries, most of them are concentrated in Internet or Web related businesses.
+Two major use of the cloud infrastructure are application host and storage service.
+However, the
 
@@
 
-\section{Massive Open Online Courses and Cloud Computing}
+\section{Education and Cloud Computing}
+At the current stage, cloud computing seems to have little interactions with education field, especially the primary and secondary educations.
+Perhaps the email system could be the only possible connections for the public schools and cloud computing, although not all the public school system will use a cloud email services from Google or Microsoft.
+My wife is a substitute teacher in Knox county school and she was a substitute teacher in Webb School at Knoxville as well.
+She tells me there is a big difference of the education philosophy and approach between Knox county school and Webb school.
+For Webb school at Knoxville, teaching has been computerized.
+The teachers prepare their course material with iPad or laptop, and every student uses an iPad in class for reading, interactions and homeworks.
+There is no physical textbooks really necessary in my wife's teaching at Webb school.
+
+In addition to the course material, Webb school has a strong IT team to support the teachers and students.
+At the new teacher training, the IT stuff at Webb school provides numerous apps inside the Apple store which could potentially benefits their teaching.
+For example, the students usually finish their homework on iPad and submit the assignment through an app, the teacher can grade it and analyze the performance of the student from its history.
+One thing I am impressed by this school is that the IT team did not create their own infrastructure in school.
+However, they use cloud computing as their complete IT infrastructure.
+For instance, the email system is provided by Google; the reading assignment system is provided by GoodReader, an impressive reading experience provider on mobile devices; student uses eBagpack as an educational Dropbox to management their study materials; and they use edmodo as a educational social network for student to vote and for teacher to post updates about the course.
+
+At present, very few schools like Webb school have the opportunity to use cloud computing to support both the school daily management and teachings/learnings.
+Let us take the Knox county school as an example.
+The school management system  and other IT infrastructure is maintained by the school's IT team.
+Perhaps it is a reliable system, but it definitely cost more than using a cloud vendor's product.
+On the other hand, the students in the public school still use textbook to learn and the teachers handle the teachings, assignments and homework traditionally.
+One of my friends, he teaches fourth grade at Knox county school.
+He is not satisfied with the current system he has in class, even though he already uses Smartboard (a computerized white board) to teach.
+He hopes to have a better tool to keep track of the student's performance throughout these years instead of using Excel.
+He thinks the cost may be one of the major reason for the school to decide build a new system.
+
+Note that the difference between independent schools and public school is not to show how well the independent school is, but to illustrate the trend of cloud computing and education which the cloud computing can help improve the education strategy.
+
+On one hand, more and more schools realize the importance of IT infrastructure in class.
+We need to teach the students how to organize the information well at the beginning.
+An easy way to start with is to teach them how to use electronic materials and make them familiar with this learning style.
+From this point of view, the schools need a new system to adapt the changes and needs, but the cost is non-trivial if every school builds their own.
+
+On the other hand, fortunately, many startups have started to build such a system under the schools' needs.
+Each individual product can be used by different schools and students that all of them actually share the same system.
+The products like eBackpack or edmodo are almost free to everyone to use or small amount of fee is charged, which definitely can reduce the cost for the schools to replace the old system.
+Besides, the cloud computing vendors can provide those startups many advantages, such as agile development and deployment, low computation and storage cost and almost zero IT maintenance cost, so that the product vendors can run their service or product at their lowest cost.
+
+In addition to the lower level education system, the cloud computing also benefits the higher education system.
+
+\section{Online-to-Offline Business and Cloud Computing}
 
@@
 
-\section{Online-to-Offline Market and Cloud Computing}
-
 \section{Conclusion}

### 2013-05-05 essay/tex/essay.tex
finish education section in essay.

@@
 Event if cloud computing had achieved so many advantages all over these years, we may notice that the current stage of cloud computing has influenced very limited industries, most of them are concentrated in Internet or Web related businesses.
-Two major use of the cloud infrastructure are application host and storage service.
-However, the
+However, we think the cloud computing could power more industries in the next $10$ year.
 
 \section{Mobile and Cloud Computing}
+The reason I first discuss the mobile technology and cloud computing is simply because I have observed the trend of the commercial electronics.
+Smartphones, tablets and ultra-books are becoming more and more popular in recent several years.
+Android and iOS powered devices attracts much more attentions than a PC or laptop.
+These devices are highly mobile, equipped with high quality camera and GPS which make the device a central hub for the multiple other equipment like camera or GPS navigators.
+Additionally, the Android and iOS app eco-system have made the smartphones much more valuable than a simple phone.
+We can see people playing Angry Birds when they are taking a bus and listening to the music when they are exercising.
+The whole category of educational apps confirm me the significance of smart devices on education.
+Therefore, it is reasonable to see the trends of mobile devices could somehow dominate the market in the future.
+
+Interestingly, if we look at the app stores, you can always see the shadows of cloud computing.
+I say ``shadow'' because there is not too many devices directly claim they belongs to cloud computing.
+But many of them use cloud computing heavily as their background support.
+For example, the new private social network app Path\cite{path} provides excellent social network experience via smartphones with close friends and families.
+Their backend systems such as data storage, machine learning/data mining and message exchanges undoubtedly depend on Amazon AWS infrastructure.
+Another example is the intelligent social media reader Prismatic\cite{prismatic} on smarthpones.
+This reader learns the user's interests and topics among numerous posts and streams online, then it starts filtering the news and presents the most relevant news to the users.
+Prismatic's app on the smartphone is very simple, but the backend systems also rely on Amazon AWS because it has to deal with large scale machine learning and realtime data service.
+These two components require super powerful computation power, reliable data storage and scalable front-end service, which is hard for a startup to build from the scratch.
+
+Furthermore, some challenges in the mobile computing are still unresolved.
+For example, the mobile network latency and battery issues which are critical to the fluency of mobile applications.
+To cope with the issues, some researchers propose the concept of \emph{Cloudlets}~\cite{satyanarayanan2009case} which bridges the mobile devices and the clouds through a middle station.
+To deal with the battery issues, some researchers proposes the \emph{offloading}~\cite{kumar2010cloud} techniques to transfer the computation from the mobile devices to the cloud.
+To speed up the mobile web browsing experience, Chrome patches the cloud speeding techniques by prefetching web pages in Google's cloud to speed up the webpage loading speed on the mobile devices.
+Therefore, we could see the cloud computing is not only a back-end supporter but a key to solve problems in mobile computing as well.
 
@@
 
-Note that the difference between independent schools and public school is not to show how well the independent school is, but to illustrate the trend of cloud computing and education which the cloud computing can help improve the education strategy.
+Note that the difference between independent schools and public school is not to show how well the independent school is, but to illustrate the trend of cloud computing and education which the cloud computing can help improve the education strategy in the next $10$ years.
 
@@
 Besides, the cloud computing vendors can provide those startups many advantages, such as agile development and deployment, low computation and storage cost and almost zero IT maintenance cost, so that the product vendors can run their service or product at their lowest cost.
+For example, Amazon AWS and Google App Engine are the most popular service providing environment for many startups.
 
-In addition to the lower level education system, the cloud computing also benefits the higher education system.
+Therefore, it is possible to expect that many companies, especially startups, could join the business to provide cheap and convenient education service in cloud to the majority of schools.
+
+In addition to the primary and secondary education system, the cloud computing also benefits the higher education system.
+Universities already have some basic infrastructure deployed in clouds.
+For example, the \emph{volmail} system in UT will be upgraded into Microsoft's Office365 platform which is Microsoft's in-cloud office software system.
+However, the cloud computing's impact in universities are not limited in IT infrastructure.
+
+Massive open online courseware (MOOC) has become a hot area in higher education recently.
+Typical companies like Coursera provides open and free online classes to students around the world.
+According to an answer from a Coursera's engineer on Quora\cite{quora2coursera}, their site relies heavily on Amazon AWS platform because each online course usually contains many videos and need a scalable student interaction platform.
+What coursera can bring to a student now is the accessibility to many different courses from various universities even if the students' universities do not open such a course.
+For example, I am taking Natural Language Processing and Probabilistic Graphic Model courses on Coursera because we do not have such courses in UT.
+But, in my opinion, MOOC is changing the way students learn knowledge.
+
+First, the students can arrange the lecture time by himself within a week so that the time does not conflict with their courses at school.
+Second, many more students register the class at once, then the analysis will give more accurate information on how well the student performs.
+Third, the professors can experiment teachings in a more flexible ways, for instance, the students can review other's assignments or projects instead of the professor himself.
+Fourth, the students can access the course materials anywhere instead of being limited in the classroom.
+
+However, my viewpoint does not necessarily mean the MOOC will replace university some day.
+In contrast, I would say never.
+One important phase in learning is the interactions between students and professors.
+Even if MOOC can provide the platform for such an interaction (not a big problem in cloud computing), the reality is that one or two professors cannot handle thousands of students at a time.
+Therefore, MOOC could be a good learning makeups in higher education to enjoy different teaching styles and viewpoints.
+Besides, the open source MOOC platform Class2Go\cite{class2go} makes it much easier for anyone who wants to make an online course for others.
 
 \section{Online-to-Offline Business and Cloud Computing}
-
-\section{Scientific Computing and Cloud Computing}
+Another part of the cloud computing's influence in the next $10$ years could be the business, especially the small business. If we look at the small busin
 

### 2013-05-06 essay/tex/essay.tex
essay draft down

@@
 \section{Online-to-Offline Business and Cloud Computing}
-Another part of the cloud computing's influence in the next $10$ years could be the business, especially the small business. If we look at the small busin
+How the business will use cloud computing in the future $10$ years is a board topic, but I am interested in the online-to-offline (O2O) business.
+In fact, most local business either have their own website to present their products to consumers online or they have use the social media to advertise itself.
+However, they do not have a complete IT infrastructure stack for their business, especially the small business.
+Medium and big companies have their IT department or some vendors will provide the service for them.
+Therefore, those companies have their website, inventory management system, and business intelligence component.
+In addition, they can use eBay or Amazon to do better marketing work.
+In contrast, if we look at the local small businesses, such as a small local antique store, they usually do not have such a complete IT infrastructure.
+Cragilist is the most common used platform for them to advertise their product; and they may buy some basic inventory management system.
+As for the business intelligence, it is almost impossible for them to take advantage of this valuable tool.
+
+The major reason for the small business to build a IT infrastructure is probably the cost.
+We cannot expect a local small store to spend thousands of dollars on the IT infrastructure, if they cannot make ten thousands of dollars profit per year.
+Fortunately, cloud computing could help them have a cheap and efficient IT infrastructure which could potentially improve their business over the years.
+
+First, in my opinion, an intelligent marketplace is critical for the local business to broadcast their products.
+Some pioneer companies have entered into this field from different angels.
+Yelp is one of the local life information search engine which provides people with local restaurant, entertainment and special offers for the smartphone users.
+The cost for listing the products is free for Yelp and extra fees are charged for premium features.
+Zarrly is another company trying to build a bi-directional marketplace so that both buyers and sellers can post information and they provide a match engine to bring potential buyers and sellers together intelligently.
+These companies take advantages of cloud computing to establish their marketplace so that the local or small businesses can spend very little money to buy their services.
+
+Second, an inventory management system and payment system are also very important to help the growth of a business.
+The typical cost of such a system is from several hundreds of dollars to thousands of dollars.
+Although the inventory management system may not be a big obstacle, the small or local business may expect an even cheaper solution.
+As for the payment system, not all local businesses support all the credit cards.
+For example, a very good Asian grocery store in Knoxville does not accept the American Express credit cards which make me very uncomfortable to buy something from their store.
+With the growing of mobile payment, companies like Google and Square has setup a convenient way to pay from smartphones or through the cloud.
+If the small stores in Knoxville can use their services, we do not need to worry about bringing cash or Visa cards before shopping in those stores.
+
+Finally, the business intelligence system seems to be impossible for the small business right for two reasons: 1) the cost usually is usually not trivial; 2) the small businesss needs to use the inventory management and payment systems to keep track of their data in store but they usually do not have a complete service ready.
+However, if cloud computing can help the inventory management and payment systems, the business intelligence component is not a big deal, because it is just another machine learning or data mining component plug into the existing system in cloud.
+
+However, the existing companies do not cover all those aspects.
+For example, eBay or Amazon could cover the intelligent marketplace, inventory management and payment system, but the business intelligence has not been under consideration yet.
+Google's Big Query is specifically for the analysis part but Google does not have a marketplace or inventory management system provided for the business.
+Even though I did not find any startups are working on the all-in-one in-cloud full stack infrastructure, but such a infrastructure from online marketplace, to inventory management, to the payment system and business intelligence could benefits the small business not only a cheap IT infrastructure but also make their whole business simpler and easier.
 
 \section{Conclusion}
+In this essay, I discussed some potential impacts that cloud computing cloud benefits for the academia and business in the next $10$ years.
+For the academia, what the primary and elementary education could benefit from cloud computing is the school IT infrastructure and teaching strategy.
+Paper-less course material and in-cloud course management system cloud replace the current ones in public school; and what the higher education could take advantages is the massive open online courseware which could bring more diversity to university students and make up unavailable courses in universities.
+On the other hand, for the business, I think the local small business could enjoy a lot from the cloud computing which could provide them an all-in-one in-cloud IT infrastructure at very low cost so that the local business could connect to both the online customers and offline ones very well.

### 2013-05-06 essay/main.tex
write education part one.
finish education section in essay.
revise mobile computing and cloud section.

--- 2013-04-26 essay/main.tex
@@
 \usepackage{cite}
+\usepackage{url}
+%\usepackage{amsmath, amsthm, amsfonts}
 \usepackage[top=1in, bottom=0.75in, left=0.75in, right=0.75in]{geometry}
-%\usepackage{pslatex}
 
@@
 \author{Jilong Liao\\jliao2@utk.edu}
-\date{\today}
 \maketitle
@@
 Major cloud computing vendors, like Amazon, Google and Dropbox, have provided users and businesses many advantages such as reliable and convenient storage, elastic computing power, and simple application deployment, lower IT infrastructure cost, etc.
-In $10$ years, I will expect cloud computing's influence far beyond the current achievements, but deeply inside mobile technology, scientific computing, massive online education and online-to-offline market.
+In $10$ years, I expect the cloud computing's influence is far beyond the current achievements.
+It should deeply inside mobile technology, education, and local small business.
 In this essay, I will discuss this point with my observations and understandings.
@@
 
-\bibliographystyle{cls/model1-num-names}
+\bibliographystyle{IEEEtran}
 \bibliography{reference}

### 2013-05-06 essay/tex/essay.tex
revise mobile computing and cloud section.

@@
 Major cloud computing vendors like Amazon, Google and Dropbox have offered the users around the world a cheap, convenient and secure computing and storage resource.
-For example, Amazon EC2 is one of the most popular cloud computing platform for many companies and individuals.
+For example, Amazon EC2\cite{garfinkel2007evaluation} is one of the most popular cloud computing platform for many companies and individuals.
 The various types of virtual instances at different price strategies provide very flexible choices for the users.
-I rent a \emph{m1.micro} instance for the use of my person website and blog for three years at a decent price around $100$ dollas.
-With the virtual instance, I do not need to install a physical machine at my home and maintain it day by day, which definitely costs more than $100$ dollas for three years.
+I rent a \emph{m1.micro} instance for the use of my person website and blog for three years at a decent price around $\$100$.
+With the virtual instance, I do not need to install a physical machine at my home and maintain it day by day, which definitely costs more than $\$100$ for three years.
 Besides individual users like me, many companies either big ones like Netflix or startups like Pinterest choose Amazon AWS as their dedicated IT infrastructure to reduce the cost of maintaining a complete IT infrastructure by themselves.
 
-An additional example of another scenario of cloud computing's application could be cloud storage.
+Another scenario of cloud computing's application could be cloud storage.
 Either Dropbox or Google Drive or Amazon Cloud Storage, they provide both companies and individuals cheap and convenient cloud storage which we do not need to worry about the data loss or accessibility.
@@
 Event if cloud computing had achieved so many advantages all over these years, we may notice that the current stage of cloud computing has influenced very limited industries, most of them are concentrated in Internet or Web related businesses.
-However, we think the cloud computing could power more industries in the next $10$ year.
+However, I think the cloud computing could power more industries in the next $10$ year.
 
 \section{Mobile and Cloud Computing}
-The reason I first discuss the mobile technology and cloud computing is simply because I have observed the trend of the commercial electronics.
+The reason I first discuss the mobile technology and cloud computing is simply because I have observed the big trend of the mobile commercial electronics.
 Smartphones, tablets and ultra-books are becoming more and more popular in recent several years.
 Android and iOS powered devices attracts much more attentions than a PC or laptop.
-These devices are highly mobile, equipped with high quality camera and GPS which make the device a central hub for the multiple other equipment like camera or GPS navigators.
+These devices are highly mobile, equipped with high quality camera and GPS which makes the device a central hub for the multiple other equipments like camera or GPS navigators.
 Additionally, the Android and iOS app eco-system have made the smartphones much more valuable than a simple phone.
@@
 The whole category of educational apps confirm me the significance of smart devices on education.
-Therefore, it is reasonable to see the trends of mobile devices could somehow dominate the market in the future.
+Therefore, it is reasonable to see the mobile devices could somehow dominate the market in the future.
 
@@
 I say ``shadow'' because there is not too many devices directly claim they belongs to cloud computing.
-But many of them use cloud computing heavily as their background support.
+But many of them use cloud computing heavily as their backend support.
 For example, the new private social network app Path\cite{path} provides excellent social network experience via smartphones with close friends and families.
@@
 Prismatic's app on the smartphone is very simple, but the backend systems also rely on Amazon AWS because it has to deal with large scale machine learning and realtime data service.
-These two components require super powerful computation power, reliable data storage and scalable front-end service, which is hard for a startup to build from the scratch.
+These two components require super powerful computation, reliable data storage and scalable front-end service, which is hard for a startup to build from the scratch.
 
 Furthermore, some challenges in the mobile computing are still unresolved.
-For example, the mobile network latency and battery issues which are critical to the fluency of mobile applications.
+For example, the mobile network latency and battery issues which are critical to the usage fluency of mobile applications.
 To cope with the issues, some researchers propose the concept of \emph{Cloudlets}~\cite{satyanarayanan2009case} which bridges the mobile devices and the clouds through a middle station.
@@
 To speed up the mobile web browsing experience, Chrome patches the cloud speeding techniques by prefetching web pages in Google's cloud to speed up the webpage loading speed on the mobile devices.
-Therefore, we could see the cloud computing is not only a back-end supporter but a key to solve problems in mobile computing as well.
+Therefore, we could see the cloud computing is not only a backend supporter but a key to solve problems in mobile computing as well.
 
@@
 
-\section{Online-to-Offline Business and Cloud Computing}
-How the business will use cloud computing in the future $10$ years is a board topic, but I am interested in the online-to-offline (O2O) business.
+\section{Local Small Business and Cloud Computing}
+How the business will use cloud computing in the future $10$ years is a board topic, but I am interested in how it will impact the local small businesses.
+
+%online-to-offline (O2O) business.
+The O2O business is the field that business connect online demands and offline convenience together, such as you can accurately discover a local product through online search or recommendation engines (sounds like an advanced e-business).
+
 In fact, most local business either have their own website to present their products to consumers online or they have use the social media to advertise itself.

### 2013-05-06 essay/tex/essay.tex
revise education section

@@
 \section{Education and Cloud Computing}
-At the current stage, cloud computing seems to have little interactions with education field, especially the primary and secondary educations.
-Perhaps the email system could be the only possible connections for the public schools and cloud computing, although not all the public school system will use a cloud email services from Google or Microsoft.
-My wife is a substitute teacher in Knox county school and she was a substitute teacher in Webb School at Knoxville as well.
-She tells me there is a big difference of the education philosophy and approach between Knox county school and Webb school.
-For Webb school at Knoxville, teaching has been computerized.
-The teachers prepare their course material with iPad or laptop, and every student uses an iPad in class for reading, interactions and homeworks.
+At the current stage, cloud computing seems to have little interactions with the education field, especially the primary and secondary educations.
+Perhaps the email system could be the only possible connections for the public schools and cloud computing, although not all the public school systems will use a cloud email services from Google or Microsoft.
+My wife was once a substitute teacher in Webb school at Knoxville and Knox county schools.
+She tells me there is a big difference of the education philosophy and approach between Webb school and Knox county school.
+For Webb school, teaching has been digitalized.
+The teachers prepare their course material with iPad or laptop, and every student uses an iPad in class for readings, interactions and homeworks.
 There is no physical textbooks really necessary in my wife's teaching at Webb school.
+In addition to the course material, Webb school has a strong IT team to support the teachers and students.
+At the new teacher training, the IT stuff at Webb school provides numerous apps inside the Apple store which could potentially benefit their teaching.
+For example, the students usually finish their homework on iPad and submit the assignment through an app.
+The teacher can grade it and analyze the performance of the student from its history very easily.
 
-In addition to the course material, Webb school has a strong IT team to support the teachers and students.
-At the new teacher training, the IT stuff at Webb school provides numerous apps inside the Apple store which could potentially benefits their teaching.
-For example, the students usually finish their homework on iPad and submit the assignment through an app, the teacher can grade it and analyze the performance of the student from its history.
 One thing I am impressed by this school is that the IT team did not create their own infrastructure in school.
 However, they use cloud computing as their complete IT infrastructure.
-For instance, the email system is provided by Google; the reading assignment system is provided by GoodReader, an impressive reading experience provider on mobile devices; student uses eBagpack as an educational Dropbox to management their study materials; and they use edmodo as a educational social network for student to vote and for teacher to post updates about the course.
+For instance, the email system is provided by Google; the reading assignments in-class are provided by GoodReader~\cite{goodreader}, an impressive reading experience provider on mobile devices; students use eBackpack~\cite{ebackpack} as an educational Dropbox to management their study materials; and they use edmodo~\cite{edmodo} as an educational social network for students to vote and for teachers to post updates about the course.
 
@@
 The school management system  and other IT infrastructure is maintained by the school's IT team.
-Perhaps it is a reliable system, but it definitely cost more than using a cloud vendor's product.
-On the other hand, the students in the public school still use textbook to learn and the teachers handle the teachings, assignments and homework traditionally.
+Perhaps it is a reliable system, but it definitely costs more than using a cloud vendor's product.
+On the other hand, the students in the public school still use textbook to learn and the teachers handle the teachings, assignments and homeworks traditionally.
 One of my friends, he teaches fourth grade at Knox county school.
-He is not satisfied with the current system he has in class, even though he already uses Smartboard (a computerized white board) to teach.
+He is not satisfied with the current computer system he has in class, even though he has already used Smartboard (a computerized white board) to teach.
 He hopes to have a better tool to keep track of the student's performance throughout these years instead of using Excel.
-He thinks the cost may be one of the major reason for the school to decide build a new system.
+He thinks the cost may be one of the major reason for the school to decide to build a new system.
 
-Note that the difference between independent schools and public school is not to show how well the independent school is, but to illustrate the trend of cloud computing and education which the cloud computing can help improve the education strategy in the next $10$ years.
+Note that the difference between independent schools and public school is not to show how well the independent schools are, but to illustrate the trend of cloud computing and education which the cloud computing can help improve the education strategy in the next $10$ years.
 
 On one hand, more and more schools realize the importance of IT infrastructure in class.
-We need to teach the students how to organize the information well at the beginning.
+We need to teach the students how to organize the massive information well at the beginning.
 An easy way to start with is to teach them how to use electronic materials and make them familiar with this learning style.
-From this point of view, the schools need a new system to adapt the changes and needs, but the cost is non-trivial if every school builds their own.
+From this point of view, the schools need a new system to adapt to the changes and needs, but the cost is non-trivial if every school builds their own.
 
 On the other hand, fortunately, many startups have started to build such a system under the schools' needs.
-Each individual product can be used by different schools and students that all of them actually share the same system.
+Each individual product can be used by different schools and students that all of them actually share the same infrastructure in cloud.
 The products like eBackpack or edmodo are almost free to everyone to use or small amount of fee is charged, which definitely can reduce the cost for the schools to replace the old system.
-Besides, the cloud computing vendors can provide those startups many advantages, such as agile development and deployment, low computation and storage cost and almost zero IT maintenance cost, so that the product vendors can run their service or product at their lowest cost.
-For example, Amazon AWS and Google App Engine are the most popular service providing environment for many startups.
+Besides, the cloud computing vendors can provide those startups many advantages, such as agile development and deployment, low computation and storage cost and almost zero IT maintenance cost, so that the product vendors can run their services or products at their lowest cost.
+For example, Amazon AWS and Google App Engine~\cite{gae} are the most popular vendors providing environment for many startups.
 
-Therefore, it is possible to expect that many companies, especially startups, could join the business to provide cheap and convenient education service in cloud to the majority of schools.
+Therefore, it is possible to expect that many companies, especially startups, could join the business to provide cheap and convenient education services in cloud to the majority of schools.
 
 In addition to the primary and secondary education system, the cloud computing also benefits the higher education system.
-Universities already have some basic infrastructure deployed in clouds.
-For example, the \emph{volmail} system in UT will be upgraded into Microsoft's Office365 platform which is Microsoft's in-cloud office software system.
-However, the cloud computing's impact in universities are not limited in IT infrastructure.
+Universities already have some basic infrastructure deployed in cloud.
+For example, the \emph{volmail} system in UT will be upgraded into Microsoft's Office365 platform~\cite{office365} which is Microsoft's in-cloud office software system.
+However, the cloud computing's impact in universities is not limited in IT infrastructure.
 
@@
 According to an answer from a Coursera's engineer on Quora\cite{quora2coursera}, their site relies heavily on Amazon AWS platform because each online course usually contains many videos and need a scalable student interaction platform.
-What coursera can bring to a student now is the accessibility to many different courses from various universities even if the students' universities do not open such a course.
+What Coursera can bring to a student now is the accessibility to many different courses from various universities even if the students' universities do not open such a course.
 For example, I am taking Natural Language Processing and Probabilistic Graphic Model courses on Coursera because we do not have such courses in UT.
@@
 First, the students can arrange the lecture time by himself within a week so that the time does not conflict with their courses at school.
-Second, many more students register the class at once, then the analysis will give more accurate information on how well the student performs.
-Third, the professors can experiment teachings in a more flexible ways, for instance, the students can review other's assignments or projects instead of the professor himself.
+Second, many more students register the class at once, then the analysis will give more accurate information on how well the students perform.
+Third, the professors can experiment teachings in a more flexible way, for instance, the students can review or grade other's assignments or projects instead of the professor himself.
 Fourth, the students can access the course materials anywhere instead of being limited in the classroom.

### 2013-05-06 essay/tex/essay.tex
revise done.

@@
 \section{Local Small Business and Cloud Computing}
-How the business will use cloud computing in the future $10$ years is a board topic, but I am interested in how it will impact the local small businesses.
+How the business will use cloud computing in the future $10$ years is a board topic, but I am interested in how cloud computing will impact the local small businesses.
 
-%online-to-offline (O2O) business.
-The O2O business is the field that business connect online demands and offline convenience together, such as you can accurately discover a local product through online search or recommendation engines (sounds like an advanced e-business).
-
-In fact, most local business either have their own website to present their products to consumers online or they have use the social media to advertise itself.
-However, they do not have a complete IT infrastructure stack for their business, especially the small business.
+In fact, most local small business either have their own website to present their products to consumers online or they use the social media to advertise themselves.
+However, they do not have a complete IT infrastructure stack for their business.
 Medium and big companies have their IT department or some vendors will provide the service for them.
 Therefore, those companies have their website, inventory management system, and business intelligence component.
-In addition, they can use eBay or Amazon to do better marketing work.
-In contrast, if we look at the local small businesses, such as a small local antique store, they usually do not have such a complete IT infrastructure.
-Cragilist is the most common used platform for them to advertise their product; and they may buy some basic inventory management system.
+In addition, they can use eBay or Amazon to do a better marketing work.
+In contrast, if we look at the local small businesses, such as a small local antique store, which usually does not have such a complete IT infrastructure.
+Cragislist is the most common used platform for them to advertise their product; and they may buy some basic inventory management system.
 As for the business intelligence, it is almost impossible for them to take advantage of this valuable tool.
 
-The major reason for the small business to build a IT infrastructure is probably the cost.
+The major reason prventing the small business to build a IT infrastructure is probably the cost.
 We cannot expect a local small store to spend thousands of dollars on the IT infrastructure, if they cannot make ten thousands of dollars profit per year.
@@
 Some pioneer companies have entered into this field from different angels.
-Yelp is one of the local life information search engine which provides people with local restaurant, entertainment and special offers for the smartphone users.
+Yelp~\cite{yelp} is one of the local life information search engine which provides local restaurant, entertainment and special offers for the smartphone users.
 The cost for listing the products is free for Yelp and extra fees are charged for premium features.
-Zarrly is another company trying to build a bi-directional marketplace so that both buyers and sellers can post information and they provide a match engine to bring potential buyers and sellers together intelligently.
-These companies take advantages of cloud computing to establish their marketplace so that the local or small businesses can spend very little money to buy their services.
+Zarrly~\cite{zarrly} is another company trying to build a bi-directional marketplace so that both buyers and sellers can post information and they use a match engine to bring potential buyers and sellers together intelligently.
+These companies take advantages of cloud computing to establish their marketplace so that the local or small businesses can spend very little money to buy their services while obtaining high quality services.
 
@@
 The typical cost of such a system is from several hundreds of dollars to thousands of dollars.
-Although the inventory management system may not be a big obstacle, the small or local business may expect an even cheaper solution.
-As for the payment system, not all local businesses support all the credit cards.
-For example, a very good Asian grocery store in Knoxville does not accept the American Express credit cards which make me very uncomfortable to buy something from their store.
-With the growing of mobile payment, companies like Google and Square has setup a convenient way to pay from smartphones or through the cloud.
+Although the inventory management system may not be a big obstacle, the local small business may expect an even cheaper solution.
+As for the payment system, not all local businesses support all types of credit cards.
+For example, a very good Asian grocery store in Knoxville does not accept the American Express credit cards which makes me very inconvenient to buy something from their store.
+With the growing of mobile payment, companies like Square~\cite{square} and Google have setup a convenient way to pay from smartphones or cloud.
 If the small stores in Knoxville can use their services, we do not need to worry about bringing cash or Visa cards before shopping in those stores.
 
-Finally, the business intelligence system seems to be impossible for the small business right for two reasons: 1) the cost usually is usually not trivial; 2) the small businesss needs to use the inventory management and payment systems to keep track of their data in store but they usually do not have a complete service ready.
-However, if cloud computing can help the inventory management and payment systems, the business intelligence component is not a big deal, because it is just another machine learning or data mining component plug into the existing system in cloud.
+Finally, the business intelligence system seems to be impossible for the small business for two reasons: 1) the cost usually is not trivial; 2) the small businesses need to use the inventory management and payment systems to keep track of their data in store but they usually do not have a complete service ready.
+Fortunately, if cloud computing can help the inventory management and payment systems, the business intelligence component is not a big deal, because it is just another machine learning or data mining component plug into the existing system in cloud.
 
@@
 For example, eBay or Amazon could cover the intelligent marketplace, inventory management and payment system, but the business intelligence has not been under consideration yet.
-Google's Big Query is specifically for the analysis part but Google does not have a marketplace or inventory management system provided for the business.
-Even though I did not find any startups are working on the all-in-one in-cloud full stack infrastructure, but such a infrastructure from online marketplace, to inventory management, to the payment system and business intelligence could benefits the small business not only a cheap IT infrastructure but also make their whole business simpler and easier.
+Google's Big Query~\cite{bigquery} is specifically for the analysis part but Google does not have a marketplace or inventory management system provided for the business.
+Even though I did not find any startups are working on the all-in-one in-cloud full stack infrastructure, but such an infrastructure from online marketplace, to inventory management, to the payment system and business intelligence could benefit the local small business not only a cheap IT infrastructure but also make their whole business simpler and easier.
 
 \section{Conclusion}
-In this essay, I discussed some potential impacts that cloud computing cloud benefits for the academia and business in the next $10$ years.
-For the academia, what the primary and elementary education could benefit from cloud computing is the school IT infrastructure and teaching strategy.
-Paper-less course material and in-cloud course management system cloud replace the current ones in public school; and what the higher education could take advantages is the massive open online courseware which could bring more diversity to university students and make up unavailable courses in universities.
+In this essay, I discussed some potential impact that cloud computing can contribute to the academia and business in the next $10$ years.
+For the academia, what the primary and elementary education could be benefit from cloud computing is the school IT infrastructure and teaching strategy.
+Paper-less course material and in-cloud course management system cloud replace the current ones in public school; and what the higher education could take advantages is the massive open online courseware which could bring more diversity to university students and make up the unavailable courses in universities.
 On the other hand, for the business, I think the local small business could enjoy a lot from the cloud computing which could provide them an all-in-one in-cloud IT infrastructure at very low cost so that the local business could connect to both the online customers and offline ones very well.

### 2013-05-06 essay/tex/essay.tex
final version

@@
 \section{Introduction}
-In recent years, cloud computing has provided us with a lot of benefits in many area.
+In recent years, cloud computing has provided us a lot of benefits in many area.
 Major cloud computing vendors like Amazon, Google and Dropbox have offered the users around the world a cheap, convenient and secure computing and storage resource.
@@
 To speed up the mobile web browsing experience, Chrome patches the cloud speeding techniques by prefetching web pages in Google's cloud to speed up the webpage loading speed on the mobile devices.
-Therefore, we could see the cloud computing is not only a backend supporter but a key to solve problems in mobile computing as well.
+Therefore, we could see the cloud computing is not only a backend supporter but a key to solve problems in mobile computing research as well.
 
 \section{Education and Cloud Computing}
-At the current stage, cloud computing seems to have little interactions with the education field, especially the primary and secondary educations.
+At the current stage, cloud computing seems to have few interactions with the education field, especially the primary and secondary educations.
 Perhaps the email system could be the only possible connections for the public schools and cloud computing, although not all the public school systems will use a cloud email services from Google or Microsoft.
